### 2018-01-13 Paper.tex
First Commit
Contains general outine for latex paper as well as a test reference section

\documentclass[conference]{IEEEtran}

%just a test references section

%use mendaly 
\begin{filecontents*}{references.bib}
	@article{Khoe:1994:CML:2288694.2294265,
		author = {Khoe, G. -D.},
		title = {Coherent multicarrier lightwave technology for flexible capacity networks},
		journal = {Comm. Mag.},
		issue_date = {March 1994},
		volume = {32},
		number = {3},
		month = mar,
		year = {1994},
		issn = {0163-6804},
		pages = {22--33},
		numpages = {12},
		url = {http://dx.doi.org/10.1109/35.267438},
		doi = {10.1109/35.267438},
		acmid = {2294265},
		publisher = {IEEE Press},
		address = {Piscataway, NJ, USA},
	}
\end{filecontents*}

\begin{document}
	\title{I am a title (RO SLAM Methods/Implementation Survey) }

	\author{David Grabowsky}

	\markboth{IEEE Transactions On xxxl, Vol. XX, No. Y, Month 2018}{Grabowsky: RO SLAM}

	\maketitle

\begin{abstract}

	This is my abstract, there are many like it, but this one is mine. Will fill this in once paper is written ****

	An survey of current the current implementations and methodologies used for solving the range only systematic and localization problem (RO-SLAM).

\end{abstract}

\section{Introduction}

\section{range only sensors/tech}
\section{Methods...}
\subsection{EKF}
%breif description (1-2 paragraphs)
%paragraphs 
The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem. The map in EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.  
%Probabilistic robotics page 312
Due to this distinction

\subsection{Graph SLAM}
\subsection{Particle}
\subsection{Graph}
\subsection{Fast}

\section{Conclusion}

	\bibliographystyle{ieeetran}
	\bibliography{references}

\end{document}

### 2018-01-14 Paper.tex
Add all the paper references to a .bib
All the papers we found should now be able to be referenced,

Just gotta go to the references.bib file and look for the key to the reference.

The references were mendaly exported

@@
 \documentclass[conference]{IEEEtran}
-
-%just a test references section
-
-%use mendaly 
-\begin{filecontents*}{references.bib}
-	@article{Khoe:1994:CML:2288694.2294265,
-		author = {Khoe, G. -D.},
-		title = {Coherent multicarrier lightwave technology for flexible capacity networks},
-		journal = {Comm. Mag.},
-		issue_date = {March 1994},
-		volume = {32},
-		number = {3},
-		month = mar,
-		year = {1994},
-		issn = {0163-6804},
-		pages = {22--33},
-		numpages = {12},
-		url = {http://dx.doi.org/10.1109/35.267438},
-		doi = {10.1109/35.267438},
-		acmid = {2294265},
-		publisher = {IEEE Press},
-		address = {Piscataway, NJ, USA},
-	}
-\end{filecontents*}
 
@@
 
+%test citation
+\cite{Blanco2008}
+
 \subsection{Graph SLAM}
@@
 
-	\bibliographystyle{ieeetran}
+	\bibliographystyle{IEEEtran}
 	\bibliography{references}

### 2018-01-15 Paper.tex
Started EKF Section
Added serveral new references, began writting EKF section.

EKF section has a rough intro,  interference pre-filtering being applied to EKF, Sum of Gaussian where each Gaussian is a compelte EKF, and beacon initalization.

@@
 The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem.
-The map in EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.
-%Probabilistic robotics page 312
-Due to this distinction
+It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments.
+\cite{Thrun2002}.
+The derivation of the EKF is very well documented, as such, detailed explanations can be seen from a variety of sources such as: \cite{Thrun2002} \cite{Ribeiro2004} \cite{Haykin2001}.
+When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.\cite{Thrun2002} This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
+This restriction means that landmarks need to be manufactured, such as those discussed in section II, and physically placed in an environment.
 
-%test citation
-\cite{Blanco2008}
+Multipathing and noise presents major obstacle to any radio frequency based RO-SLAM solutions.
+Research and experimentation has been conducted to determine how these effects can be mitigated without the use of specialized equipment.
+Fabreese presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
+The author also validates this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+\cite{Fabresse2016}.
+
+%fabreese. 
+%1. 2013 presents EKF slam method for ariel vehicles 
+%2. 2014 introduces prefiltering to measurments for previous 
+%3. 2014a integrates visual landmakrs as well
+%4  2015 decentralized multiple arieal vehicles
+%5  2016 specifically unmaned ariel, experimental validation.
+
+Vallicrosa presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
+The filter makes use the EKF by representing each Gaussian in the SOG as a complete EKF, results are given in a simulated environment.\cite{Vallicrosa2015}
+
+One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF is especially sensitive to poorly initialized landmarks.
 

### 2018-01-15 Paper.tex
Added more to ekf section
Added a part about a robust range only localization by Olson and some grammer edits

@@
 \cite{Thrun2002}.
-The derivation of the EKF is very well documented, as such, detailed explanations can be seen from a variety of sources such as: \cite{Thrun2002} \cite{Ribeiro2004} \cite{Haykin2001}.
+The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002} \cite{Ribeiro2004} \cite{Haykin2001}.
 When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.\cite{Thrun2002} This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
 This restriction means that landmarks need to be manufactured, such as those discussed in section II, and physically placed in an environment.
+
+A system for robust range only localiztion was prosed by Olson \cite{Olson2006}.
+The system utilized an Autonomous Underwater Vehicle (AUV) and beacons without carefully surveyed locations.
+A method for outliers rejection was accomplished via spectral graph partitioning.
+A voting scheme was implemented similar to a Hugh transform to get approximate beacon locations \cite{Hough1959}.
+The approximate location was then incorporated into an EKF.
+The methodology was simulated using a dataset from the GOAT'02 experiment.
+%get a citaion for goat.
 
@@
 Fabreese presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
-The author also validates this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+The author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
 \cite{Fabresse2016}.
@@
 %4  2015 decentralized multiple arieal vehicles
-%5  2016 specifically unmaned ariel, experimental validation.
+%5  2016 specifically unmaned ariel, experimental validation of 2013,2014.
 
 Vallicrosa presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
-The filter makes use the EKF by representing each Gaussian in the SOG as a complete EKF, results are given in a simulated environment.\cite{Vallicrosa2015}
+The filter made use the EKF by representing each Gaussian in the SOG as a complete EKF \cite{Vallicrosa2015}.
+Results are given from a simulated environment.
+
+Several techniques have also been implemented that involve cooperative sensors. The sensors in these cases are able to determine the range between themselves and other sensors and or the robot.
+%ADD MORE HERE
+In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
+He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
+In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated is open.
+
+Torres-Gonzalez explains that methods utilizing inter beacon measurment should incorporate measurements with a configurable number of hops between beacons.
+This allows for the robot to gather range data from beyond the extent of the robots sensors \cite{Torres-Gonzalez2015}.
+Based on testing with an EKF, his results showed that the more hops that were added the greater the performance of the system.
 

### 2018-01-15 Paper.tex
Added some more to EKF section
added a few more references and paragraphs to ekf section

@@
 The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem.
-It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments.
-\cite{Thrun2002}.
+It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments \cite{Thrun2002}.
 The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002} \cite{Ribeiro2004} \cite{Haykin2001}.
@@
 This restriction means that landmarks need to be manufactured, such as those discussed in section II, and physically placed in an environment.
+Landmark initilization is a critical element in many algorithms that make use of the EKF.
+If the initialization is inaccurate then the convergence to a correct estimation becomes more difficult.
 
-A system for robust range only localiztion was prosed by Olson \cite{Olson2006}.
+A system for robust range only localization was prosed by Olson \cite{Olson2006}.
 The system utilized an Autonomous Underwater Vehicle (AUV) and beacons without carefully surveyed locations.
@@
 The approximate location was then incorporated into an EKF.
-The methodology was simulated using a dataset from the GOAT'02 experiment.
+The methodology was simulated using a dataset from the GOAT'02 experiment and can be seen in the report.
 %get a citaion for goat.
@@
 %4  2015 decentralized multiple arieal vehicles
-%5  2016 specifically unmaned ariel, experimental validation of 2013,2014.
+%5  2016 specifically unmaned ariel, more details on 2013,2014 and experimental validation of 2013,2014.
 
 Vallicrosa presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
-The filter made use the EKF by representing each Gaussian in the SOG as a complete EKF \cite{Vallicrosa2015}.
+The filter made use of the EKF by representing each Gaussian in the SOG as a complete EKF \cite{Vallicrosa2015}.
 Results are given from a simulated environment.
 
-Several techniques have also been implemented that involve cooperative sensors. The sensors in these cases are able to determine the range between themselves and other sensors and or the robot.
+Several techniques have also been implemented that involve cooperative sensors.
+The sensors in these cases are able to determine the range between themselves and other sensors and or the robot.
+\cite{Patwari2005}
 %ADD MORE HERE
@@
 He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
-In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated is open.
+In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated was available.
 
@@
 
-One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF is especially sensitive to poorly initialized landmarks.
+One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF is sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+Caballero presents a solution for this complication.
+\cite{Caballero2010}.
+A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
+This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks.
+Ahmad proposes to reduce the computational burden of methods such as the one mentioned before by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters  \cite{Ahmad2011a}.
+Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
+
+Djugash proposes an extension to EKF called relative-over parametrized (ROP) EKF.
+This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM.
+\cite{Djugash2008}.
+ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
+The method provided improved results over EKF when sparse range measurment of data association errors were present.
+Herranz presents a comparison of the ROP-EKF method presented by Djugash \cite{Djugash2008},to a smoothing and mapping method presented by Dellaert \cite{Dellaert2006}.
+Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP-EKF.
+\cite{Herranz2014}
+
+The first, known as ROP-EKF [8], is
+an extension of the standard EKF to formulate the SLAM
+problem in polar coordinates.
 

### 2018-01-16 Paper.tex
Even more stuff added to EKF
Up to a page and a half and 20 references.

Also added a folder to store and figures in (the current figure path is busted and will be fixed later)

@@
 \documentclass[conference]{IEEEtran}
+\usepackage{graphicx}
+%\graphicspath{Figures}
 
@@
 It is used to overcome the assumption of linear state transitions and measurements, which are rarely seen in practical environments \cite{Thrun2002}.
-The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002} \cite{Ribeiro2004} \cite{Haykin2001}.
+The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002}, \cite{Ribeiro2004}, and \cite{Haykin2001}.
 When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.\cite{Thrun2002} This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
-This restriction means that landmarks need to be manufactured, such as those discussed in section II, and physically placed in an environment.
-Landmark initilization is a critical element in many algorithms that make use of the EKF.
+This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment.
+Landmark initialization is a critical element in many algorithms that make use of the EKF.
 If the initialization is inaccurate then the convergence to a correct estimation becomes more difficult.
@@
 Research and experimentation has been conducted to determine how these effects can be mitigated without the use of specialized equipment.
-Fabreese presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
+Fabresse presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
 The author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
@@
 Several techniques have also been implemented that involve cooperative sensors.
-The sensors in these cases are able to determine the range between themselves and other sensors and or the robot.
-\cite{Patwari2005}
+The sensors in these cases are able to determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=90mm]{coop_loc_comp_patwari.png}
+	\caption{Traditional(a) vs Cooperative(b) Sensors \cite{Patwari2005}}
+	\label{trad_vs_coop_sensors}
+\end{figure}
+
 %ADD MORE HERE
@@
 A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
-This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks.
-Ahmad proposes to reduce the computational burden of methods such as the one mentioned before by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
+Geneve
+%fix the name
+ also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used \cite{Geneve2015}.
+Ahmad proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
 The paper proposes that under different circumstances the landmark could be represented using different parameters  \cite{Ahmad2011a}.
 Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
+The results showed that when the circumstances can be clearly distinguished between an increase in performance is seen.
 
@@
 ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
-The method provided improved results over EKF when sparse range measurment of data association errors were present.
+The method provided improved results over EKF when sparse range measurement of data association errors were present.
 Herranz presents a comparison of the ROP-EKF method presented by Djugash \cite{Djugash2008},to a smoothing and mapping method presented by Dellaert \cite{Dellaert2006}.
-Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP-EKF.
+Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
 \cite{Herranz2014}
 
-The first, known as ROP-EKF [8], is
-an extension of the standard EKF to formulate the SLAM
-problem in polar coordinates.
+A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem.
+The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in.
+The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}.
+%this one might need some more work
+
+\cite{Fabresse2013} presents a solution for the 3D RO-SLAM problem.
+The solution reduces computational load through reduced spherical parametrization of map feature positions.
+The paper also proposes a new EKF update method which incorporates a reduced spherical representation of the state vector.
+In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse}.
+
+%2015 (decentrailzied) works off 2013 (undelayed)
 

### 2018-01-16 Paper.tex
Quick Fix
Error in .bib was causing compilation crashes, quickly fixed it and added a little bit to EKF section

@@
 The paper also proposes a new EKF update method which incorporates a reduced spherical representation of the state vector.
-In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse}.
+In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}.
+It is proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors.
+This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
 

### 2018-01-16 Paper.tex
Added figure path
added path to figures in Figure folder to tex file

@@
 \usepackage{graphicx}
-%\graphicspath{Figures}
+\graphicspath{{Figures/}}
 
@@
 ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=90mm]{ROP_djugash.png}
+	\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row).
+True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated.
+\cite{Djugash2008}} %THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+	\label{ROP_djugash}
+\end{figure}
+
 The method provided improved results over EKF when sparse range measurement of data association errors were present.

### 2018-01-18 Paper.tex
Test
Test commit
Mergre Test
particle filter methods

@@
 This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
+I am a test.
 
@@
 \subsection{Particle}
+Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]).
+In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
+It is considered better and more robost to conventional estimtion methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimentional problems
+%Description
+Initially robot assumes global uncertainity through a set of particles that are distributed all over the map.
+Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
+There are several resampling methods depending on computational complexities.
+After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks
+Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution p($x_o$).
+Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in (x^[i])_(t-1)
+
 \subsection{Graph}
-\subsection{Fast}
+\subsection{Fast SLAM}
+%Brief introduction
+
+%advantages
+%Disadvantages
 

### 2018-01-18 Paper.tex
Added placeins package, and EKF section stuff
Added placeins package to help with precise figure placement

Also added more to EKF

--- 2018-01-16 Paper.tex
@@
 \usepackage{graphicx}
+\usepackage{placeins}
 \graphicspath{{Figures/}}
@@
 This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment.
-Landmark initialization is a critical element in many algorithms that make use of the EKF.
+However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized.
+Initialization is a critical element in many algorithms that make use of the EKF.
 If the initialization is inaccurate then the convergence to a correct estimation becomes more difficult.
+The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
+This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via EKF.
 
-A system for robust range only localization was prosed by Olson \cite{Olson2006}.
+A system for robust range only localization was prosed by \cite{Olson2006}.
 The system utilized an Autonomous Underwater Vehicle (AUV) and beacons without carefully surveyed locations.
-A method for outliers rejection was accomplished via spectral graph partitioning.
+The paper notes that one of the majors issue was noise present in the received data.
+A method for outliers rejection caused by the noise was accomplished via spectral graph partitioning.
 A voting scheme was implemented similar to a Hugh transform to get approximate beacon locations \cite{Hough1959}.
 The approximate location was then incorporated into an EKF.
-The methodology was simulated using a dataset from the GOAT'02 experiment and can be seen in the report.
-%get a citaion for goat.
+It is noted by the paper that this method is particularly CPU intensive, however they state that since the rate at which data is acquired from a landmark is slow, every 5 or so seconds, then the AUV can afford the expensive computation since there will be an adequate amount of time between readings for the data to process.
+The methodology was simulated using a dataset and can be seen in the report.
+
+\cite{Kurth2003} presents a comparison of how three methods process a collected data set.
+The methods are a EKF, a sliding batch, and a particle filter.
+The comparison considers the cross-track error, and along track error.
+The results state that the particle filter works well when used to acquire an initial pose estimate, and EKF works well with real-time localization.
+It is suggested that in the future that the two could be switched between when appropriate to improve the overall system.
 
@@
 Research and experimentation has been conducted to determine how these effects can be mitigated without the use of specialized equipment.
-Fabresse presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
-The author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
-\cite{Fabresse2016}.
+\cite{Fabresse2014} presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects.
+In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
 
@@
 
-Vallicrosa presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
-The filter made use of the EKF by representing each Gaussian in the SOG as a complete EKF \cite{Vallicrosa2015}.
-Results are given from a simulated environment.
+\cite{Vallicrosa2015} presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
+It uses multivariate Gaussian mixtures to represent the probability distribution functions of the robot and beacon positions as Gaussian particles which each contain an EKF for vehicle position, velocity, and estimated beacon position.
+The paper presented experimentation where the method was used to map a beacon while correcting the navigation of the vehicle.
 
 Several techniques have also been implemented that involve cooperative sensors.
-The sensors in these cases are able to determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
-
+Traditionally sensors were used to only determine the range between themselves and the robot.
+The sensors in these cases provide the ability determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
 \begin{figure}[h!]
@@
 \end{figure}
-
-%ADD MORE HERE
-In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
-He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
-In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated was available.
+\FloatBarrier
 
@@
 Based on testing with an EKF, his results showed that the more hops that were added the greater the performance of the system.
+
+In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
+He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
+In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated was available.
 
@@
 This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
-Geneve
-%fix the name
-also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used \cite{Geneve2015}.
-Ahmad proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
-The paper proposes that under different circumstances the landmark could be represented using different parameters  \cite{Ahmad2011a}.
+\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used.
+\cite{Ahmad2011a} proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters.
 Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
@@
 True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated.
-\cite{Djugash2008}} %THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+\cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
 	\label{ROP_djugash}
 \end{figure}
+\FloatBarrier
 
@@
 The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}.
+The first mode is noted as mapping (MS) and the second localization (LS).
+When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations.
+Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
 	%this one might need some more work
@@
 This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
+Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot.
 
-%2015 (decentrailzied) works off 2013 (undelayed)
+Kehagias explores how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at.
+\cite{Kehagias2006} The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
+The results provided show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
 
@@
 \subsection{Graph}
-\subsection{Fast}
+\subsection{Fast SLAM}
 

### 2018-01-18 Paper.tex

@@
 \subsection{Particle}
+Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]).
+In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
+It is considered better and more robost to conventional estimtion methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimentional problems
+%Description
+Initially robot assumes global uncertainity through a set of particles that are distributed all over the map.
+Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
+There are several resampling methods depending on computational complexities.
+After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks
+Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution p($x_o$).
+Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in (x^[i])_(t-1)
+
 \subsection{Graph}
 \subsection{Fast SLAM}
+%Brief introduction
+
+%advantages
+%Disadvantages
 

### 2018-01-19 Paper.tex
Added some more stuff to the ignore
ignore .aux, .log, .pdf. synctex.gz.

Also, note 100% sure how that last merge happened since there were no other commits...
Added some final(maybe) touches to EKF section
Added the final parts to EKF section and did a quick proof read of it.

@@
 The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002}, \cite{Ribeiro2004}, and \cite{Haykin2001}.
-When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation.\cite{Thrun2002} This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
+When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation \cite{Thrun2002}.
+This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
 This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment.
@@
 Initialization is a critical element in many algorithms that make use of the EKF.
-If the initialization is inaccurate then the convergence to a correct estimation becomes more difficult.
+If the initialization is inaccurate then the convergence to a correct estimation becomes much more difficult for the filter.
 The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
@@
 A voting scheme was implemented similar to a Hugh transform to get approximate beacon locations \cite{Hough1959}.
-The approximate location was then incorporated into an EKF.
-It is noted by the paper that this method is particularly CPU intensive, however they state that since the rate at which data is acquired from a landmark is slow, every 5 or so seconds, then the AUV can afford the expensive computation since there will be an adequate amount of time between readings for the data to process.
-The methodology was simulated using a dataset and can be seen in the report.
+The approximate locations were then incorporated into an EKF.
+It is noted by the paper that this method is particularly CPU intensive, however they state that since the rate at which data is acquired from a landmark is slow, every 5 or so seconds, that the AUV can afford the expensive computation since there will be an adequate amount of time between readings for the data to process.
+The methodology was simulated using a dataset and can be seen in the paper.
 
@@
 It is suggested that in the future that the two could be switched between when appropriate to improve the overall system.
-
-Multipathing and noise presents major obstacle to any radio frequency based RO-SLAM solutions.
-Research and experimentation has been conducted to determine how these effects can be mitigated without the use of specialized equipment.
-\cite{Fabresse2014} presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects.
-In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
 
@@
 
-Torres-Gonzalez explains that methods utilizing inter beacon measurment should incorporate measurements with a configurable number of hops between beacons.
-This allows for the robot to gather range data from beyond the extent of the robots sensors \cite{Torres-Gonzalez2015}.
-Based on testing with an EKF, his results showed that the more hops that were added the greater the performance of the system.
+It is explained by \cite{Torres-Gonzalez2015} that methods utilizing inter beacon measurment should incorporate measurements with a configurable number of hops between beacons.
+This allows for the robot to gather range data from beyond the extent of the robots sensors.
+Experimentations was conducted utilizing this method via a particle filter EKF.
+The results showed that the more hops that were added the greater the performance of the system.
 
-In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
+\cite{Djugash2006} presents a comparison of multiple RO SLAM methods utilized in two scenarios.
+One scenario involves the case where the robot only has access to range information between itself and beacons at unknown locations.
+In the second case the robot also has access to information about beacon to beacon distances.
+Several separate methods were compared in the given scenarios utilizing a data set and experimentation.
+The first method utilizes the Kalman filter in the case where only measurment between moving and stationary beacons are considered.
+Another method specifically uses the beacon to beacon measurements with an online Kalman filter.
+An off line batch method is used to get an estimate of the beacon location and robot path.
+Finally an method that considers the robot as a virtual node for creating submaps to be solved with a multidimensional scaling algorithm is also considered.
+The paper gives experimental results and analysis for each of the methods.
+
+%In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all every other landmarks, \cite{Djugash2006} presents a solution.
 He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
@@
 
-Djugash proposes an extension to EKF called relative-over parametrized (ROP) EKF.
+An extension to EKF called relative-over parametrized (ROP) EKF is presented by \cite{Djugash2008}.
 This extension uses specific parameterization to  better represent the range only data utilized in RO-SLAM.
-\cite{Djugash2008}.
 ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
+The method provided improved results over EKF when sparse range measurement of data association errors were present.
+\cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}e{Djugash2008},to a smoothing and mapping method presented by \cite{Dellaert2006}.
+Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
 \begin{figure}[h!]
@@
 True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated.
-\cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+\cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS?%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
 	\label{ROP_djugash}
@@
 \FloatBarrier
-
-The method provided improved results over EKF when sparse range measurement of data association errors were present.
-Herranz presents a comparison of the ROP-EKF method presented by Djugash \cite{Djugash2008},to a smoothing and mapping method presented by Dellaert \cite{Dellaert2006}.
-Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
-\cite{Herranz2014}
 
@@
 
+It is explored by \cite{Kehagias2006} how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at and then applied to solve the RO SLAM problem.
+The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
+The results provided show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
+
 \cite{Fabresse2013} presents a solution for the 3D RO-SLAM problem.
@@
 In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}.
-It is proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors.
+In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipathing.
+It is then proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors.
 This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
 Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot.
-
-Kehagias explores how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at.
-\cite{Kehagias2006} The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
-The results provided show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
+In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
 
@@
 Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution p($x_o$).
-Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in (x^[i])_(t-1)
+Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in $(x^[i])_(t-1)$
 

### 2018-01-19 Paper.tex
Particle filter update

--- 2018-01-18 Paper.tex
@@
 \usepackage{graphicx}
-\usepackage{placeins}
 \graphicspath{{Figures/}}
@@
 This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment.
-However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized.
-Initialization is a critical element in many algorithms that make use of the EKF.
+Landmark initialization is a critical element in many algorithms that make use of the EKF.
 If the initialization is inaccurate then the convergence to a correct estimation becomes more difficult.
-The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
-This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via EKF.
 
-A system for robust range only localization was prosed by \cite{Olson2006}.
+A system for robust range only localization was prosed by Olson \cite{Olson2006}.
 The system utilized an Autonomous Underwater Vehicle (AUV) and beacons without carefully surveyed locations.
-The paper notes that one of the majors issue was noise present in the received data.
-A method for outliers rejection caused by the noise was accomplished via spectral graph partitioning.
+A method for outliers rejection was accomplished via spectral graph partitioning.
 A voting scheme was implemented similar to a Hugh transform to get approximate beacon locations \cite{Hough1959}.
 The approximate location was then incorporated into an EKF.
-It is noted by the paper that this method is particularly CPU intensive, however they state that since the rate at which data is acquired from a landmark is slow, every 5 or so seconds, then the AUV can afford the expensive computation since there will be an adequate amount of time between readings for the data to process.
-The methodology was simulated using a dataset and can be seen in the report.
-
-\cite{Kurth2003} presents a comparison of how three methods process a collected data set.
-The methods are a EKF, a sliding batch, and a particle filter.
-The comparison considers the cross-track error, and along track error.
-The results state that the particle filter works well when used to acquire an initial pose estimate, and EKF works well with real-time localization.
-It is suggested that in the future that the two could be switched between when appropriate to improve the overall system.
+The methodology was simulated using a dataset from the GOAT'02 experiment and can be seen in the report.
+%get a citaion for goat.
 
@@
 Research and experimentation has been conducted to determine how these effects can be mitigated without the use of specialized equipment.
-\cite{Fabresse2014} presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects.
-In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+Fabresse presents a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce these effects \cite{Fabresse2014}.
+The author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+\cite{Fabresse2016}.
 
@@
 
-\cite{Vallicrosa2015} presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
-It uses multivariate Gaussian mixtures to represent the probability distribution functions of the robot and beacon positions as Gaussian particles which each contain an EKF for vehicle position, velocity, and estimated beacon position.
-The paper presented experimentation where the method was used to map a beacon while correcting the navigation of the vehicle.
+Vallicrosa presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
+The filter made use of the EKF by representing each Gaussian in the SOG as a complete EKF \cite{Vallicrosa2015}.
+Results are given from a simulated environment.
 
 Several techniques have also been implemented that involve cooperative sensors.
-Traditionally sensors were used to only determine the range between themselves and the robot.
-The sensors in these cases provide the ability determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
+The sensors in these cases are able to determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
+
 \begin{figure}[h!]
@@
 \end{figure}
-\FloatBarrier
+
+%ADD MORE HERE
+In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
+He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
+In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated was available.
 
@@
 Based on testing with an EKF, his results showed that the more hops that were added the greater the performance of the system.
-
-In scenarios where the location of the landmarks is unknown and each landmark can not communicate with all other landmarks, Djugash presents a solution.
-He proposes that a moving beacon be used to add edges to the network \cite{Djugash2006}.
-In addition, no external position sensing were required on the part of the moving beacon, but the option for it to be incorporated was available.
 
@@
 This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
-\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used.
-\cite{Ahmad2011a} proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
-The paper proposes that under different circumstances the landmark could be represented using different parameters.
+Geneve
+%fix the name
+also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used \cite{Geneve2015}.
+Ahmad proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters  \cite{Ahmad2011a}.
 Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
@@
 True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated.
-\cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+\cite{Djugash2008}} %THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
 	\label{ROP_djugash}
 \end{figure}
-\FloatBarrier
 
@@
 The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}.
-The first mode is noted as mapping (MS) and the second localization (LS).
-When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations.
-Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
 %this one might need some more work
@@
 This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
-Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot.
+I am a test.
 
-Kehagias explores how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at.
-\cite{Kehagias2006} The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
-The results provided show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
+%2015 (decentrailzied) works off 2013 (undelayed)
 
 \subsection{Graph SLAM}
-\subsection{Particle}
+\subsection{Particle}      %change the references
+Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]).
+In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
+It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems
+%Description
+Initially robot assumes global uncertainity through a set of particles that are distributed all over the map.
+Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
+There are several resampling methods depending on computational complexities.
+After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
+	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter.
+The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations.
+Only the particles which have a higher probability are re sampled.
+The image on the right shows the particle filter eventually converging to estimate the robot location.
+}
+
+\end{figure}
+Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution $ p(x_o)$.
+Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$.
+It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$.
+Eventually the particle filter converges to give us the true positioning of the robot.
+
+As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization and also higher dimensional localization problem.
+
 \subsection{Graph}
 \subsection{Fast SLAM}
+%Brief introduction
+
+%advantages
+%Disadvantages
 

### 2018-01-19 Paper.tex
latest particle filter complete

--- 2018-01-19 Paper.tex
@@
 \documentclass[conference]{IEEEtran}
+
 \usepackage{graphicx}
+
 \usepackage{placeins}
+
 \graphicspath{{Figures/}}
@@
 \begin{document}
+
 	\title{I am a title (RO SLAM Methods/Implementation Survey) }
@@
 	\section{range only sensors/tech}
+
 	\section{Methods...}
+
 	\subsection{EKF}
+
 	%breif description (1-2 paragraphs)
+
 	%paragraphs
+
 	The Extended Kalman Filter (EKF) is one of the most popular and widespread methods used to solve the SLAM problem.
@@
 	%fabreese.
+
 	%1. 2013 presents EKF slam method for ariel vehicles
+
 	%2. 2014 introduces prefiltering to measurments for previous
+
 	%3. 2014a integrates visual landmakrs as well
+
 	%4  2015 decentralized multiple arieal vehicles
+
 	%5  2016 specifically unmaned ariel, more details on 2013,2014 and experimental validation of 2013,2014.
@@
 The sensors in these cases provide the ability determine the range between themselves and other sensors and or the robot \cite{Patwari2005}.
+
 	\begin{figure}[h!]
+
 		\centering
+
 		\includegraphics[width=90mm]{coop_loc_comp_patwari.png}
+
 		\caption{Traditional(a) vs Cooperative(b) Sensors \cite{Patwari2005}}
+
 		\label{trad_vs_coop_sensors}
+
 	\end{figure}
+
 	\FloatBarrier
@@
 Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
+
 	\begin{figure}[h!]
+
 		\centering
+
 		\includegraphics[width=90mm]{ROP_djugash.png}
+
 		\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row).
@@
 \cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS?%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+
 		\label{ROP_djugash}
+
 	\end{figure}
+
 	\FloatBarrier
@@
 Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
+
 	%this one might need some more work
@@
 	\subsection{Graph SLAM}
-\subsection{Particle}
+
+\subsection{Particle}      %change the references
 Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]).
 In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robost to conventional estimtion methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimentional problems
+It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems
 %Description
@@
 There are several resampling methods depending on computational complexities.
-After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks
-Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution p($x_o$).
-Once the robot starts moving it collects measurements and at time t$>$0 we sample a new particle set $x^[i]_t$ for each partile in $(x^[i])_(t-1)$
+After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
+	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter.
+The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations.
+Only the particles which have a higher probability are re sampled.
+The image on the right shows the particle filter eventually converging to estimate the robot location.
+}
+
+\end{figure}
+Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution $ p(x_oa)$.
+resampling methods depending on computational complexities.
+After some iterations only th   p
+Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$.
+It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$.
+Eventually the particle filter converges to give us the true positioning of the robot.
+
+As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem form[14]) where the robot is randomly picked up and placed in a unknown environment.
+EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[thusn book[]
+As the number of particles increases the computational complexity of the filter too increases.
+In order to address this there were several new methods introduced that  exploit the independence among state variables.
+For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity.
+from [Fast slam paper].
+It also solves the data association problem previously unsolved by EKF.[8]
 
 	\subsection{Graph}
+
 	\subsection{Fast SLAM}
+
 	%Brief introduction
@@
 	%advantages
+
 	%Disadvantages
@@
 	\bibliographystyle{IEEEtran}
+
 	\bibliography{references}

### 2018-01-19 Paper.tex
Created beacon initalization section
created beacon initalization second and moved some of the ekf beacon stuff into it

@@
 	\section{range only sensors/tech}
+
+	\section{Beacon Initialization}
+	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation.
+TOne of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+Caballero presents a solution for this complication.
+\cite{Caballero2010}.
+A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
+This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
+\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used.
+\cite{Ahmad2011a} proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters.
+Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
+The results showed that when the circumstances can be clearly distinguished between an increase in performance is seen.
 

### 2018-01-19 Paper.tex
Finished EKF added Range only sensros stuff, added beacon initizlation
EKF Section: 'done' and waiting review/edits

Range Only Sensors section: hesitantly done and in need of in depth review

Beacon Initialization: added the ekf section to it, waiting on other sectons

--- 2018-01-19 Paper.tex
@@
 
-	\section{Methods...}
+	One of the key features of the systematic localization and mapping problem are landmarks.
+In RO SLAM the only information that can be obtained from landmarks is range data.
+This range data must then be interpreted by the robot in some way that will be advantageous towards the localization and mapping process.
+Beacons are a popular implementation of landmarks.
+Beacons refer to any devices which involves a signal transmission that can be used for the localization and mapping process without line of sight.
+The most popular beacons can largely be broken down into two categories: acoustic based and radio frequency based.
+
+	\subsection{Acoustic}
+
+	Acoustic ranging systems are primary used with robotics and beacons that operate in underwater locations.
+The reason for this that radio waves experience strong attenuations, especially in salt water environments.
+As \cite{Partan2007} states, the issue of attenuations makes radio waves extremely impractical, thus making acoustics the logical alternative.
+Acoustic still suffer from a range of problems such as multipathing and propagation delays, but are one of the only meaningful alternatives.
+Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issue and possible techniques that relate to acoustic sensors, such as the added complexity of assuming a 2D environment vs a 3D environment, or design challenge that accompany underwater deployment like spatial correlation and power.
+
+	An interesting beacon for underwater localization that is not specifically range only or acoustic based is the Dive'N'Rise (DNR) beacons presented by \cite{Erol2007}.
+These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates.
+The distance to an agent and the transmitting beacon can be determined via time of flight from the transmissions.
+A localization implementation using these beacons was accomplished by \cite{Erol2008}.
+Again while this is not purely range only or acoustic based it was found to be interesting solution worth mentioning.
+
+  	\begin{figure}[h!]
+
+	\centering
+
+	\includegraphics[width=90mm]{DNR.png}
+
+	\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
+
+	\label{DNR}
+
+\end{figure}
+
+	\subsection{Radio Frequency}
+	Radio frequency encompass a massive spectrum of devices capable of transmitting or receiving transmission on the radio frequency.
+There are two methods primarily utilized to determine distance from radio frequency.
+One is by examining the received signal strength indicator (RSSI) and the other is the by measuring the time of flight of the signal.
+A system presented by \cite{Padmanabhan2000} processes rf signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.
+\cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.
+As a robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond to.
+The robot then estimates the distance to the tag based on the delay.
+The response from the RF tags include a data tag which contains a unique ID number.
+
+	Wireless sensors networks (WSN) are also a very popular choice, especially since many of them come with the ability to transmit RSSI.
+\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each presents surveys relating to WSNs.
+\cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed survey that discuss hardware, protocols, standards, security, energy efficiency and much more.
+\cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards.
+\cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations.
+\cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.
+
+	%blue tooth
+
+	%wifi
+
+	%Fingerprint map based on radiological patterns
+	%P. Bahl and V. Padmanabhan, “Radar: A, in-building rf-based user
+	%location and tracking system,” in Proc. of the IEEE Infocom, 2000,
+	%pp. 775–784.
+
+	%M. Oca ̃na, L. M. Bergasa, M. A. Sotelo, R. F. Flores, D. F.  ́
+	%Llorca, and D. Schleicher, “Automatic training method applied to
+	a% WiFi+ultrasound POMDP navigation system,” Robotica, vol. 27,
+	%no. 07, pp. 1049–1061, December 2009.
+
+	%rfid
+	%Mapping and localization with RFID technology
+
+	\section{Beacon Initialization}
+	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation.
+One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+\cite{Caballero2010} presents a solution for this complication.
+A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
+This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
+\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane.
+\cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters.
+Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
+The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.
+
+	\section{Methods and Their Implementations}
 
@@
 This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
-This restriction means that landmarks often need to be manufactured, such as those discussed in section II, and physically placed in an environment.
+This restriction means that landmarks often need to be manufactured, such as the beacons discussed in previous sections, and physically placed in an environment.
 However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized.
@@
 The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
-This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via EKF.
+This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via methods with EKF mind.
 
@@
 
-	One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF is sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
-Caballero presents a solution for this complication.
-\cite{Caballero2010}.
-A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
-This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
-\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane are used.
-\cite{Ahmad2011a} proposes to reduce the computational burden of methods such as the one proposed by Caballero \cite{Caballero2010} by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
-The paper proposes that under different circumstances the landmark could be represented using different parameters.
-Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
-The results showed that when the circumstances can be clearly distinguished between an increase in performance is seen.
-
 	An extension to EKF called relative-over parametrized (ROP) EKF is presented by \cite{Djugash2008}.
@@
 ROP EKF operates in polar coordinates as opposed to the Cartesian space that typical EKF operates.
-The method provided improved results over EKF when sparse range measurement of data association errors were present.
-\cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}e{Djugash2008},to a smoothing and mapping method presented by \cite{Dellaert2006}.
-Experimentation conducted by Herranz on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
+The method provided improved results over EKF when sparse range measurement or data association errors were present.
+\cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}, to a smoothing and mapping method presented by \cite{Dellaert2006}.
+Experimentation conducted by \cite{Herranz2014} on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
 
@@
 
-		\caption{True and approximated distributions with one range observation (Top Row) and two observations from different locations (Bottom Row).
-True distributions in	Cartesian coordinates (Left Column), true and Gaussian approximated distributions in polar coordinates (Middle Column), and projection of the Gaussian approximated.
-\cite{Djugash2008}} LITERALLY COPIED, CHANGE DIS?%THIS WAS LITTERALY COPYIED AND PASTED AND NEEDS TO BE CHANGED AT SOME POINTS
+		\caption{Top Row: True and approximated distribution from one range observation.
+Bottom Row: True and approximated distributions with two observations from different locations.
+Left Column: Distribution in Cartesian Coordinates.
+Middle Column: True and Gaussian approximated distributions in Polar Coordinates, Right Column: Projection of the Gaussian approximated.
+\cite{Djugash2008}}
 
@@
 	\end{figure}
-
-	\FloatBarrier
 
@@
 When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations.
-Based on experimentation performed by \cite{Dios2015} the method performed well an a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
+Based on experimentation performed by \cite{Dios2015} the method performed well and a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
 
@@
 The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
-The results provided show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
+The results provided by the paper show that the interpolation based algorithms gave better landmark estimation than those without, with the exception of the EKF in two datasets where EKF was already performing poorly.
 

### 2018-01-19 Paper.tex
with SPEIF

--- 2018-01-19 Paper.tex
@@
 
+	\subsection{Sparse Extended Information Filters}
+	Need to add references
+
+	Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
+In EKF the gaussians are represented in the form of their moments; mean and 	variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
+Hence they are dual to each other.
+	Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
+This makes the SEIF more scalable and effiecient as show in [SEIF paper1]
+
+	The information filter stores the relation between any 2 state elements in the information matrix also known as links.
+The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state .
+SEIF maintains a sparse information matrix by elimatinating weak inks that are below a certain threshold thus reducing the computational complexity involved .
+
+	In [SEIF PAER 1] they furthur reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
+Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
+Hence the computer burden on the robot is reduced.
+In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
+	In conclusion this menthod ahad better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+
 	\subsection{Graph SLAM}
@@
 In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems
+It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems [38]in AI.
 %Description
@@
 As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem form[14]) where the robot is randomly picked up and placed in a unknown environment.
-EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[thusn book[]
+EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[thusn book]
 As the number of particles increases the computational complexity of the filter too increases.
-In order to address this there were several new methods introduced that  exploit the independence among state variables.
+In order to address this there were several new methods introduced that  exploit the conditional independence[37] among state variables.
 For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity.

### 2018-01-25 Paper.tex
Stupid forced merge

--- 2018-01-19 Paper.tex
@@
 One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+Poorly approximated landmarks results in the divergence of the filter.
+These processes are furthur  divided into delayed and undelayed initializations.
+	\subsection{Delayed initializations}
+	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
+Localization can be performed only once a accurate estimations of the beacons are made.
+There are several methods that achieve this.
+	\subsubsection{Trilateration}
+	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
+	\subsubsection{Particle filter}
+
 	\cite{Caballero2010} presents a solution for this complication.
@@
 	\subsection{Fast SLAM}
+	EKF is mainly used when we have a non-linear dynamic system model which has gaussian noise.[1]-[3].The quadratic complexity due to gaussian approximations of higher dimensions make the covariance matrix very large.
+This eventually cqauses higher complexity and leads to the divergence of the filter.The single data association problem also adds to this complexity.
+FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem.
+Thi allows it handle system models with non gaussians noise as well.
+This results in the computatoinal complexity to grow logarithmically instead of quadratic growth.
+
+	FastSLAM utilizes the conditional Independence property of SLAM applications.
+If the path of the robot is known the correlation between the landmarks becomes zero.
+Hence in FastSLAM the robot path is initialised by using a particle fitler.
+Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in [Fast Slam paper 1].
+Thus it maintains mutliple data hypothesis overcoming the EKF problem.
+
+	$p(x^{k}_(1:t)$
 

### 2018-01-25 Paper.tex
Revert "with SPEIF"
Messed up a previous commit/merge. This should fix everything... prabably...

--- 2018-01-19 Paper.tex
@@
 
-	\includegraphics[width=90mm]{DNR.png}
+%	\includegraphics[width=90mm]{DNR.png}
 

### 2018-01-26 Paper.tex
Added Abstract and Part of Introduction

@@
 
-	\title{I am a title (RO SLAM Methods/Implementation Survey) }
+	\title{A Survey of Range-Only SLAM Techniques and Sensors}
 
-	\author{David Grabowsky}
+	\author{David Grabowsky, Samyak Shetty, Sam Shue, James M. Conrad}
 
@@
 	\begin{abstract}
-
-		This is my abstract, there are many like it, but this one is mine. Will fill this in once paper is written ****
-
-		An survey of current the current implementations and methodologies used for solving the range only systematic and localization problem (RO-SLAM).
-
+		 A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM).
+In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, within the environment through sensors such as cameras and laser rangefinders.
+Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation proses of the robot's pose and the landmark locations within the map.
+However, some applications use landmarks which are only capable of providing range information, such as wireless and acoutstic beacons.
+In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors (RO-SLAM) is explored.
 	\end{abstract}
@@
 	\section{Introduction}
+
+	The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications.
+SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information.
+The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is with respect to a global frame, or map, and building a map requires knowledge of the robot's location.
+There are many algorithms used to solve this problem, most using a landmark-based approach.
+The concept of a landmark is identifying a distinguishable feature in the environment through camera or laser rangefinder and estimating the distance and orientation of that landmark relative to the robot.
+Then, as the robot traverses the environment, it can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
+In most SLAM applications, references to the map is synonymous with the locations of the landmarks.
+
+	In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry.
+While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors.
+However, GPS isn't available in all environments, such as indoors and underwater.
+Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively.
+While these beacons provide sensor information to the robotic vehicle, they don't inherently provide location information unless their positions are accurately known beforehand and are certain to never change.
+Wireless and sonar beacons are capable of providing range measurements instead.
 
@@
 
-%	\includegraphics[width=90mm]{DNR.png}
+	\includegraphics[width=90mm]{DNR.png}
 
@@
 One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
-Poorly approximated landmarks results in the divergence of the filter.
-These processes are furthur  divided into delayed and undelayed initializations.
-	\subsection{Delayed initializations}
-	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
-Localization can be performed only once a accurate estimations of the beacons are made.
-There are several methods that achieve this.
-	\subsubsection{Trilateration}
-	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
-	\subsubsection{Particle filter}
-
 \cite{Caballero2010} presents a solution for this complication.
@@
 	\subsection{Fast SLAM}
-	EKF is mainly used when we have a non-linear dynamic system model which has gaussian noise.[1]-[3].The quadratic complexity due to gaussian approximations of higher dimensions make the covariance matrix very large.
-This eventually cqauses higher complexity and leads to the divergence of the filter.The single data association problem also adds to this complexity.
-FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem.
-Thi allows it handle system models with non gaussians noise as well.
-This results in the computatoinal complexity to grow logarithmically instead of quadratic growth.
-
-	FastSLAM utilizes the conditional Independence property of SLAM applications.
-If the path of the robot is known the correlation between the landmarks becomes zero.
-Hence in FastSLAM the robot path is initialised by using a particle fitler.
-Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in [Fast Slam paper 1].
-Thus it maintains mutliple data hypothesis overcoming the EKF problem.
-
-	$p(x^{k}_(1:t)$
 

### 2018-01-26 Paper.tex

@@
 	\includegraphics[width=90mm]{DNR.png}
+%	\includegraphics[width=90mm]{DNR.png}
 
@@
 One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+\cite{Caballero2010} presents a solution for this complication.
+A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
+This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
+\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane.
+\cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
+The paper proposes that under different circumstances the landmark could be represented using different parameters.
+Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
+The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.
+	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation.
+One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+Poorly approximated landmarks results in the divergence of the filter.
+These processes are furthur  divided into delayed and undelayed initializations.
+	\subsection{Delayed initializations}
+	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
+Localization can be performed only once a accurate estimations of the beacons are made.
+There are several methods that achieve this.
+	\subsubsection{Trilateration}
+	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
+	\subsubsection{Particle filter}
+
 	\cite{Caballero2010} presents a solution for this complication.

### 2018-01-26 Paper.tex
removed .txt and .bib from git ignore
lets try not to make any more change to the git ignore
Completed intialisations
Added intializations ans the seif part. Still need to redo paragraphs and add references.

--- 2018-01-25 Paper.tex
@@
 These processes are furthur  divided into delayed and undelayed initializations.
-	\subsection{Delayed initializations}
-	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
+	\subsection{Delayed/Offline initializations}
+	These are the intialisations where  therobots moves around offline collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
 Localization can be performed only once a accurate estimations of the beacons are made.
 There are several methods that achieve this.
+There are several offline algorithms that perform localization such as the least squares approach in[5 of Active range only beacon lov=calisationi],a posed based ekf as mentioned in[8] , a moving horizon estimation as mentioned in [9] etc.
+The most popular ones are mentioned below
 	\subsubsection{Trilateration}
-	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
+	[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique where a basic  circle intersection technique.
+The rings are drawn at different points of the robots path , where the radius of the rings depends on the strength of the received sginal from the beacon.
+This method of intilizatio is highly ambiguous as the rings can have more than 1 point of intersecting  or no points intersecting.
+%more paperes needed
 	\subsubsection{Particle filter}
+	This takes a more probabilistic approach to estimating the initial location of the beacons.
+As mentioned in[thrun particle filter paper] initially the entire space is represented by particles.
+These particles are resampled based on importance weights every iteration.
+Eventually the particle set converges to a accurate location of the beacons.
+Though this method of localization can be computationally expensive it is preferred where the noise involved is non Gaussian.
 
-	\cite{Caballero2010} presents a solution for this complication.
+	\subsection{Undelayed/Online initializations}
+	In this case the robot both initializes and localizes itself and the beacons as it moves.
+	as mentioned in \cite{Caballero2010}.
 A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
@@
 
+\subsection{Sparse Extended Information Filters}
+Need to add references
+
+Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
+In EKF the gaussians are represented in the form of their moments; mean and 	variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
+Hence they are dual to each other.
+Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
+This makes the SEIF more scalable and effiecient as show in [SEIF paper1]
+
+The information filter stores the relation between any 2 state elements in the information matrix also known as links.
+The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state .
+SEIF maintains a sparse information matrix by elimatinating weak inks that are below a certain threshold thus reducing the computational complexity involved .
+
+In [SEIF PAER 1] they furthur reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
+Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
+Hence the computer burden on the robot is reduced.
+In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
+In conclusion this menthod ahad better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+
 	\subsection{Graph}

### 2018-01-26 Paper.tex
Readding: Added Abstract and Part of Introduction
Everything should be fixed now.

@@
 
-		This is my abstract, there are many like it, but this one is mine. Will fill this in once paper is written ****
-
-		An survey of current the current implementations and methodologies used for solving the range only systematic and localization problem (RO-SLAM).
+A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM).
+In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, within the environment through sensors such as cameras and laser rangefinders.
+Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation proses of the robot's pose and the landmark locations within the map.
+However, some applications use landmarks which are only capable of providing range information, such as wireless and acoutstic beacons.
+In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors (RO-SLAM) is explored.
 
@@
 	\section{Introduction} 
+		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications.
+SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information.
+The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is with respect to a global frame, or map, and building a map requires knowledge of the robot's location.
+There are many algorithms used to solve this problem, most using a landmark-based approach.
+The concept of a landmark is identifying a distinguishable feature in the environment through camera or laser rangefinder and estimating the distance and orientation of that landmark relative to the robot.
+Then, as the robot traverses the environment, it can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
+In most SLAM applications, references to the map is synonymous with the locations of the landmarks.
+
+	In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry.
+While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors.
+However, GPS isn't available in all environments, such as indoors and underwater.
+Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively.
+While these beacons provide sensor information to the robotic vehicle, they don't inherently provide location information unless their positions are accurately known beforehand and are certain to never change.
+Wireless and sonar beacons are capable of providing range measurements instead.
 
@@
 	\centering
+
+%	\includegraphics[width=90mm]{DNR.png}
 

### 2018-01-29 Paper.tex
initialization and SEIF
blah blah
with trilateration diagram

@@
 Poorly approximated landmarks results in the divergence of the filter.
-These processes are furthur  divided into delayed and undelayed initializations.
+These methods are further  divided into delayed and undelayed initializations.
 \subsection{Delayed/Offline initializations}
-	These are the intialisations where  therobots moves around offline collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application.
+These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks.
+This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles.
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several methods that achieve this.
 There are several offline algorithms that perform localization such as the least squares approach in[5 of Active range only beacon lov=calisationi],a posed based ekf as mentioned in[8] , a moving horizon estimation as mentioned in [9] etc.
-The most popular ones are mentioned below
+The most popular ones are mentioned below.
+
+\begin{figure}
+	\centering
+	\includegraphics[height=40mm,width=90mm]{Trilateration_methods.JPG}
+	\caption{The red arrow represents the robot.The 'X' represents the origin of the robot. The blue line shows the traversed path.The star represents the landmark. }
+
+\end{figure}
 \subsubsection{Trilateration}
-	[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique where a basic  circle intersection technique.
-The rings are drawn at different points of the robots path , where the radius of the rings depends on the strength of the received sginal from the beacon.
-This method of intilizatio is highly ambiguous as the rings can have more than 1 point of intersecting  or no points intersecting.
+[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique involving geometric intersection.
+Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons.
+This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c].
 %more paperes needed
@@
 These particles are resampled based on importance weights every iteration.
-Eventually the particle set converges to a accurate location of the beacons.
-Though this method of localization can be computationally expensive it is preferred where the noise involved is non Gaussian.
+There are several resampling methods mentioned in[methods paper].
+Eventually the particle set converges to the accurate location of the beacons.
+Though this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
 
 \subsection{Undelayed/Online initializations}
-	In this case the robot both initializes and localizes itself and the beacons as it moves.
+In this case the robot simultaneously initializes and localizes itself and the beacons as it moves
 as mentioned in \cite{Caballero2010}.
@@
 
+\subsection{Sparse Extended Information Filters}
+Need to add references
+
+Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
+An IF algorithm is mentioned in[ probobilistic robotics book].
+In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
+Hence they are dual to each other.
+Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
+This makes the SEIF more scalable and effiecient as show in [SEIF paper1]
+
+The information filter stores the relation between any 2 state elements in the information matrix also known as links.
+The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state .
+SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved .
+
+In [SEIF PAER 1] they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
+Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
+Hence the computer burden on the robot is reduced.
+In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
+In [seif paper 2] it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+
 	\subsection{Graph SLAM}
@@
 \subsection{Particle}      %change the references
-Particles filters are made ue up various monte carlo algorithms that are used to estimate states in partially observable Markov chains(see[9]).
-In the initial application of particle filters in the field of robotics was in localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14].It has also been at the corre higher dimensional problems
+Particles filters are made ue up various monte carlo algorithms.
+they are used to estimate states in partially observable Markov chains as shown in [9].
+In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
+It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14] which EKF in comparison has it drawbacks.
+It has also been at the core higher dimensional computational problems.
 %Description
@@
 Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
-There are several resampling methods depending on computational complexities.
-After some iterations only the particles which have a high degree of probability  reamain and eventually converge to the state of the robot and the landmarks.
+There are several resampling methods depending on computational complexities[sampling methods paper].
+After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
 \begin{figure}[h!]
@@
 
-As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem form[14]) where the robot is randomly picked up and placed in a unknown environment.
-EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[thusn book[]
+As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment.
+EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[probablistic robotics]
 As the number of particles increases the computational complexity of the filter too increases.
 In order to address this there were several new methods introduced that  exploit the independence among state variables.
-For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity.
-from [Fast slam paper].
-It also solves the data association problem previously unsolved by EKF.[8]
-
-\subsection{Sparse Extended Information Filters}
-Need to add references
-
-Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
-In EKF the gaussians are represented in the form of their moments; mean and 	variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
-Hence they are dual to each other.
-Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
-This makes the SEIF more scalable and effiecient as show in [SEIF paper1]
-
-The information filter stores the relation between any 2 state elements in the information matrix also known as links.
-The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state .
-SEIF maintains a sparse information matrix by elimatinating weak inks that are below a certain threshold thus reducing the computational complexity involved .
-
-In [SEIF PAER 1] they furthur reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
-Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
-Hence the computer burden on the robot is reduced.
-In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
-In conclusion this menthod ahad better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
-
-	\subsection{Graph}
+For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper].
+It also solves the data association problem previously unsolved by EKF[8].
 
 	\subsection{Fast SLAM}
-	EKF is mainly used when we have a non-linear dynamic system model which has gaussian noise.[1]-[3].The quadratic complexity due to gaussian approximations of higher dimensions make the covariance matrix very large.
-This eventually cqauses higher complexity and leads to the divergence of the filter.The single data association problem also adds to this complexity.
+	EKF is mainly used when we have a non-linear dynamic system model which has Gaussian noise.The quadratic complexity due to Gaussian approximations of higher dimensions make the covariance matrix very large.
+This eventually causes higher complexity and leads to the divergence of the filter.
+The single data association problem also adds to this complexity.
 FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem.
-Thi allows it handle system models with non gaussians noise as well.
-This results in the computatoinal complexity to grow logarithmically instead of quadratic growth.
+This allows it handle system models with non gaussians noise as well.
+This results in the computational complexity to grow logarithmically instead of quadratic growth.
 
@@
 
-	$p(x^{k}_(1:t)$
+	As mentioned in [probablisitic robotics] the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency.
+In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0.
+It was called the Rao-Blackwellized particle filter as mentioned in[fast slam 2]
 

### 2018-01-29 Paper.tex
Graph slam

@@
 
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=70mm,width=90mm]{graph_slam.PNG}
+	\caption{$z_k,\mu_k,x_k$ represents the measurement contraints, velocity constraints and the the robot path.}
+
+\end{figure}
+
 \subsection{Graph SLAM}
+Graph SLAM unlike the EKF solves the full SLAM problem.
+It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix.
+The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in[Probablisitic robotics].
+This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.
+
+It represents the information in the form of a graph as show in figure.
+The nodes in the graph represent the robots path and the landmarks.
+The edges between them represents the spatial  constraints between them also known as information constraints.
+These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in [ turorial in graph slam].
 

### 2018-02-05 Paper.tex
edits

@@
 \section{Beacon Initialization}
-Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation.
-One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated.
+One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
 Poorly approximated landmarks results in the divergence of the filter.
@@
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in[5 of Active range only beacon lov=calisationi],a posed based ekf as mentioned in[8] , a moving horizon estimation as mentioned in [9] etc.
+There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman2003},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc.
 The most popular ones are mentioned below.
@@
 In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
-In [seif paper 2] it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+In \cite{Djugash2006} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
 

### 2018-02-05 Paper.tex

@@
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman2003},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc.
+There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc.
 The most popular ones are mentioned below.
@@
 \subsubsection{Trilateration}
-[Pure Porbablisitc approach to RO  SLAM] mentions a basic trilateration technique involving geometric intersection.
+\cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection.
 Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons.
@@
 This takes a more probabilistic approach to estimating the initial location of the beacons.
-As mentioned in[thrun particle filter paper] initially the entire space is represented by particles.
+As mentioned in\cite{Thrun2002a} initially the entire space is represented by particles.
 These particles are resampled based on importance weights every iteration.
-There are several resampling methods mentioned in[methods paper].
+There are several resampling methods mentioned in \cite{Li2015}.
 Eventually the particle set converges to the accurate location of the beacons.
@@
 Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
-An IF algorithm is mentioned in[ probobilistic robotics book].
+An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}.
 In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
@@
 Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
-This makes the SEIF more scalable and effiecient as show in [SEIF paper1]
+This makes the SEIF more scalable and effiecient as show in\cite{Torres-Gonzalez2014}
 
@@
 
-In [SEIF PAER 1] they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
+In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
 Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
@@
 In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
-In \cite{Djugash2006} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
 
@@
 It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix.
-The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in[Probablisitic robotics].
+The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in\cite{Thrun2002a}.
 This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.
@@
 Particles filters are made ue up various monte carlo algorithms.
-they are used to estimate states in partially observable Markov chains as shown in [9].
+they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}.
 In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem[14] which EKF in comparison has it drawbacks.
+It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks.
 It has also been at the core higher dimensional computational problems.
@@
 Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
-There are several resampling methods depending on computational complexities[sampling methods paper].
-After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
+There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
 \begin{figure}[h!]
@@
 As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment.
-EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information[probablistic robotics]
+EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
 As the number of particles increases the computational complexity of the filter too increases.
@@
 For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper].
-It also solves the data association problem previously unsolved by EKF[8].
+It also solves the data association problem previously unsolved by EKF[need to add paper].
 
@@
 Hence in FastSLAM the robot path is initialised by using a particle fitler.
-Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in [Fast Slam paper 1].
+Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{}.
 Thus it maintains mutliple data hypothesis overcoming the EKF problem.
 
-	As mentioned in [probablisitic robotics] the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency.
+	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency.
 In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0.
-It was called the Rao-Blackwellized particle filter as mentioned in[fast slam 2]
+It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}
 

### 2018-02-05 Paper.tex
Latest

@@
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{} , a moving horizon estimation as mentioned in [9] etc.
+There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster} , a moving horizon estimation as mentioned in \cite{SenWang2013} etc.
 The most popular ones are mentioned below.
@@
 Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
-This makes the SEIF more scalable and effiecient as show in\cite{Torres-Gonzalez2014}
+This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}
 
@@
 In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
-In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this menthod had better estimates and lesser computational burden than the traditionl RO SLAM mehtod using EKF.
+In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM mehtod using EKF.
 
@@
 The edges between them represents the spatial  constraints between them also known as information constraints.
-These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in [ turorial in graph slam].
+These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.
 
@@
 
-As mentioned in[thrun particle] particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment.
+As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment.
 EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
@@
 In order to address this there were several new methods introduced that  exploit the independence among state variables.
-For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from [Fast slam paper].
-It also solves the data association problem previously unsolved by EKF[need to add paper].
+For example the Rao-Blackwellized particle filters that exploit the independence of the landmarks with the robot path thereby reducing the computation complexity from \cite{Yuan2012}.
+It also solves the data association problem previously unsolved by EKF.
 
@@
 Hence in FastSLAM the robot path is initialised by using a particle fitler.
-Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{}.
+Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}.
 Thus it maintains mutliple data hypothesis overcoming the EKF problem.

### 2018-02-05 Paper.tex
Spelling corrections

@@
 The first mode is noted as mapping (MS) and the second localization (LS).
-When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations.
+When in mapping mode the measurement are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations.
 Based on experimentation performed by \cite{Dios2015} the method performed well and a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.
@@
 In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}.
-In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipathing.
+In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurement before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipath.
 It is then proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors.
@@
 An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}.
-In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
+In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the Gaussians in their conical parameterization which comprises of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
 Hence they are dual to each other.
-Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix.
+Sparse Extended information filters is derived from the  information filter but it maintains a sparse representation of the information matrix.
 This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}
@@
 The information filter stores the relation between any 2 state elements in the information matrix also known as links.
-The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state .
+The higher the value of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robots state.
 SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved .
@@
 In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
-Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process.
+Here the robot computes the prediction stage of the iteration, send the information to the beacons where they compute the update of the process.
 Hence the computer burden on the robot is reduced.
-In addition they factored in inter beacon measurements to reduce uncertainity even furthur.
-In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM mehtod using EKF.
+In addition, they factored in inter beacon measurements to reduce uncertainty even further.
+In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.
 
@@
 The edges between them represents the spatial  constraints between them also known as information constraints.
-These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.
+These constraints ae then linearized and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.
 
@@
 %Description
-Initially robot assumes global uncertainity through a set of particles that are distributed all over the map.
+Initially robot assumes global uncertainty through a set of particles that are distributed all over the map.
 Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
@@
 \end{figure}
-Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution $ p(x_oa)$.
-resampling methods depending on computational complexities.
+Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.
+re sampling methods depending on computational complexities.
 After some iterations only th   p
@@
 FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem.
-This allows it handle system models with non gaussians noise as well.
+This allows it handle system models with non Gaussians noise as well.
 This results in the computational complexity to grow logarithmically instead of quadratic growth.
@@
 If the path of the robot is known the correlation between the landmarks becomes zero.
-Hence in FastSLAM the robot path is initialised by using a particle fitler.
+Hence, in FastSLAM the robot path is initialized by using a particle filter.
 Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}.
-Thus it maintains mutliple data hypothesis overcoming the EKF problem.
+Thus, it maintains multiple data hypothesis overcoming the EKF problem.
 
-	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency.
-In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0.
+	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficiency.
+In order to overcome this the algorithm was tweaked to have a better target distribution in FASTSLAM 2.0.
 It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}

### 2018-02-11 Paper.tex
Added Introduction

@@
 
-	\author{David Grabowsky, Samyak Shetty, Sam Shue, James M. Conrad}
+	\author{\IEEEauthorblockN{David Grabowsky\IEEEauthorrefmark{1}, Samyak Shetty\IEEEauthorrefmark{2}, Sam Shue\IEEEauthorrefmark{3}, James M. Conrad}
+		\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
+			University of North Carolina at Charlotte\\
+			Charlotte, NC, USA\\
+			\IEEEauthorrefmark{1}dgrabows@uncc.edu, \IEEEauthorrefmark{2}nshetty@uncc.edu, \IEEEauthorrefmark{3} slshue@uncc.edu, \IEEEauthorrefmark{4}jmconrad@uncc.edu}
+	}
 
@@
 	\begin{abstract}		
-
 		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM).
@@
 In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors (RO-SLAM) is explored.
-
 	\end{abstract}
@@
 Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively.
-While these beacons provide sensor information to the robotic vehicle, they don't inherently provide location information unless their positions are accurately known beforehand and are certain to never change.
-Wireless and sonar beacons are capable of providing range measurements instead.
+While these beacons provide distance estimations to the robotic vehicle, they do not inherently provide location information as with GPS.
+However, these distances are often still useful as they can be used to compensate for the drift that occurs from measuring a vehicle's displacement through integration of inertial sensor readings.
+Most SLAM algorithms utilize these range values as a corrective measurement, the same way traditional algorithms use sensed landmarks.
+However, rather than using range and orientation to landmarks, beacons are only capable of providing range.
+SLAM algorithms which utilize these beacons are referred to as Range-Only SLAM (RO-SLAM).
 
-	\section{range only sensors/tech}
+		While the loss of orientation from traditional, vision based landmarks prevents refinement of the robot's orientation, range only beacons solve two major problems encountered in traditional landmark-based approaches: landmark association and landmark scaling.
+The landmark association problem occurs when a detected landmark has similar features to previously recorded landmark and is mistaken for the other, generating huge errors in the estimation of both the robot and the landmark.
+This problem is avoided using beacons, as they have some kind of network address which is broadcast during transmissions, so there is no way to confuse which range is associated with which landmark.
+The scaling problem occurs when a SLAM algorithm runs for a long time and more and more landmarks are appended to the map.
+As more landmarks are added, the amount of memory needed to store the positions and distributions of these landmarks increases, as well as computation time.
+When using beacons, a finite number of landmarks exists, and the total size of the map is known before deployment.
+In addition, fewer landmarks are needed in beacon-based applications, as most beacons do not require line-of-sight to be measured, unlike visual landmarks.
+Since the robot can observe the landmarks more often, it doesn't need to add nearly as many to ensure accurate position estimation.
 
-	One of the key features of the systematic localization and mapping problem are landmarks.
-In RO SLAM the only information that can be obtained from landmarks is range data.
-This range data must then be interpreted by the robot in some way that will be advantageous towards the localization and mapping process.
-Beacons are a popular implementation of landmarks.
-Beacons refer to any devices which involves a signal transmission that can be used for the localization and mapping process without line of sight.
+		This paper surveys the most popular techniques in RO-SLAM applications.
+Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of these beacons in Section \ref{beacon initialization}.
+Solutions to the RO-SLAM state estimation problem are covered in Section \ref{methods and their implementations}.
+Finally, the conclusion in Section \ref{conclusion} closes with final thoughts regarding the state of the field of RO-SLAM.
+
+	\section{range only sensors}
+	\label{range only sensors}
+		There are a variety of range sensors which can be utilized as beacons for RO-SLAM.
+Beacons refer to any device which involves a signal transmission that can be used for the range estimation without line of sight.
 The most popular beacons can largely be broken down into two categories: acoustic based and radio frequency based.
+These beacons serve as landmarks within larger SLAM algorithms.
+The following section surveys the different types of sensors which can be utilized as range beacons.
 
@@
 
-	Acoustic ranging systems are primary used with robotics and beacons that operate in underwater locations.
+			Acoustic ranging systems are primarily used with autonomous underwater vehicles (AUV) and sonar beacons that operate in underwater locations.
 The reason for this that radio waves experience strong attenuations, especially in salt water environments.
@@
 Acoustic still suffer from a range of problems such as multipathing and propagation delays, but are one of the only meaningful alternatives.
-Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issue and possible techniques that relate to acoustic sensors, such as the added complexity of assuming a 2D environment vs a 3D environment, or design challenge that accompany underwater deployment like spatial correlation and power.
+Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a 2D environment versus a 3D environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.
 
-	An interesting beacon for underwater localization that is not specifically range only or acoustic based is the Dive'N'Rise (DNR) beacons presented by \cite{Erol2007}.
+			A unique implementation of an underwater acoustic beacon is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}.
 These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates.
@@
 A localization implementation using these beacons was accomplished by \cite{Erol2008}.
-Again while this is not purely range only or acoustic based it was found to be interesting solution worth mentioning.
 
 			  	\begin{figure}[h!]
-
 					\centering
-
 				%	\includegraphics[width=90mm]{DNR.png}
-
 				%	\includegraphics[width=90mm]{DNR.png}	
-
 					\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
-
 					\label{DNR}
-
 				\end{figure}
@@
 One is by examining the received signal strength indicator (RSSI) and the other is the by measuring the time of flight of the signal.
-A system presented by \cite{Padmanabhan2000} processes rf signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.
+A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.
 \cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.
-As a robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond to.
+As a mobile robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond.
 The robot then estimates the distance to the tag based on the delay.
@@
 			Wireless sensors networks (WSN) are also a very popular choice, especially since many of them come with the ability to transmit RSSI.
-\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each presents surveys relating to WSNs.
-\cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed survey that discuss hardware, protocols, standards, security, energy efficiency and much more.
+\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.
+\cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more.
 \cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards.
@@
 	\section{Beacon Initialization}
-Beacons initialization refers to the precursor process to the EKF where beacons (or landmarks) whose initial positions are not known are estimated.
-One of the complications with RO-SLAM involves the issue of the EKF, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
+		\label{beacon initialization}
+		The core motivation of SLAM algorithms is no a priori knowledge of the operating environment.
+This includes locations of landmarks, including beacons.
+Because of this, landmarks are appended to the map as they are discovered in traditional SLAM algorithms, using the robot's estimated pose and the sensed distance and orientation to estimate an initial position of the landmark.
+The landmark's positions is then refined as the algorithm continues to run.
+
+		The same process occurs in RO-SLAM, however, the landmark's initial position is not so easily determined, as the range-only beacon has an unknown orientation relative to the robot.
+Therefore, the landmark could reside approximately anywhere within the sensed distance radius.
+To compensate for this, most beacons go through an initialization phase before being appended to the map and utilized in the RO-SLAM algorithm.
+This initialization phase is usually performed over several iterations until the position converges to an acceptable degree.
+
+		One RO-SLAM complication in particular involves the issue of EKF-SLAM, which is used by many implementations, being  sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate.
 Poorly approximated landmarks results in the divergence of the filter.
-These methods are further  divided into delayed and undelayed initializations.
+
+		Presented here are the most effective and commonly used methods to initialize range beacons. These methods are further divided into delayed and undelayed initializations.
+
 		\subsection{Delayed/Offline initializations}
@@
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster} , a moving horizon estimation as mentioned in \cite{SenWang2013} etc.
+There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster}, a moving horizon estimation as mentioned in \cite{SenWang2013} etc.
 The most popular ones are mentioned below.
@@
 			\caption{The red arrow represents the robot.The 'X' represents the origin of the robot. The blue line shows the traversed path.The star represents the landmark. }
+		\end{figure}
 
-\end{figure}
 	\subsubsection{Trilateration}
@@
 This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c].
-%more paperes needed
+%more papers needed
+
 	\subsubsection{Particle filter}
@@
 	\section{Methods and Their Implementations}
+	\label{methods and their implementations}
 
@@
 	\section{Conclusion}
+	\label{conclusion}
 

### 2018-02-14 Paper.tex
Added UWB and WIFI section
added a UWB and WIFI paragraph, also rephrased to WSN section to focus more on the fact that several surveys exist for specific things (zigbee, 802,etc)

@@
 
-			  	\begin{figure}[h!]
-					\centering
+	%		  	\begin{figure}[h!]
+	%				\centering
 				%	\includegraphics[width=90mm]{DNR.png}
 	%				\includegraphics[width=90mm]{DNR.png}	
-					\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
-					\label{DNR}
-				\end{figure}
+	%				\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
+	%				\label{DNR}
+	%			\end{figure}
 
@@
 
-			Wireless sensors networks (WSN) are also a very popular choice, especially since many of them come with the ability to transmit RSSI.
-\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.
+			Ultra-wideband radios are another popular choice.
+One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms.
+\cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
+
+			Wireless Fidelity (wi-fi)  is another choice being explored by man researchers as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
+\cite{Youssef2005} presents a Horus system with the aim of high accuracy and low computation cost for wireless local area network location determining.
+\cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing.
+\cite{Kotaru2015} presents a design and implementation for its SpotFi system which can be deployed on top of existing wi-fi infrastructure.
+\cite{Rea2017} designed a new method for filtering range measurment specifically designed with the large noise found in indoor WiFi radios in mind.
+
+			 \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to wireless sensor networks.
 \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more.
@@
 			%Llorca, and D. Schleicher, “Automatic training method applied to
-			a% WiFi+ultrasound POMDP navigation system,” Robotica, vol. 27,
+			% WiFi+ultrasound POMDP navigation system,” Robotica, vol. 27,
 			%no. 07, pp. 1049–1061, December 2009.

### 2018-02-14 Paper.tex
Deleting graph and fast salm

@@
 Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster}, a moving horizon estimation as mentioned in \cite{SenWang2013} etc.
+There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman}, a posed based ekf as mentioned in \cite{Webster2012}, a moving horizon estimation as mentioned in \cite{Vallicrosa2014a} etc.
 The most popular ones are mentioned below.
@@
 		\cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection.
-Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons.
+Rings are drawn at different points of the robots path as shown in Fig[a], where the radius of the rings depend on the strength of the received signals from the beacons.
 This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c].
@@
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[height=70mm,width=90mm]{graph_slam.PNG}
-	\caption{$z_k,\mu_k,x_k$ represents the measurement contraints, velocity constraints and the the robot path.}
-
-\end{figure}
-
-\subsection{Graph SLAM}
-Graph SLAM unlike the EKF solves the full SLAM problem.
-It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix.
-The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in\cite{Thrun2002a}.
-This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.
-
-It represents the information in the form of a graph as show in figure.
-The nodes in the graph represent the robots path and the landmarks.
-The edges between them represents the spatial  constraints between them also known as information constraints.
-These constraints ae then linearized and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.
-
-\subsection{Particle}      %change the references
+\subsection{Particle Filters}      %change the references
 Particles filters are made ue up various monte carlo algorithms.
@@
 
-	\subsection{Fast SLAM}
-	EKF is mainly used when we have a non-linear dynamic system model which has Gaussian noise.The quadratic complexity due to Gaussian approximations of higher dimensions make the covariance matrix very large.
-This eventually causes higher complexity and leads to the divergence of the filter.
-The single data association problem also adds to this complexity.
-FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem.
-This allows it handle system models with non Gaussians noise as well.
-This results in the computational complexity to grow logarithmically instead of quadratic growth.
-
-	FastSLAM utilizes the conditional Independence property of SLAM applications.
-If the path of the robot is known the correlation between the landmarks becomes zero.
-Hence, in FastSLAM the robot path is initialized by using a particle filter.
-Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}.
-Thus, it maintains multiple data hypothesis overcoming the EKF problem.
-
-	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficiency.
-In order to overcome this the algorithm was tweaked to have a better target distribution in FASTSLAM 2.0.
-It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}
+In /cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
+It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small.
+This approach is validated for both simulated and real data sets.
+This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.
 

### 2018-02-14 Paper.tex
with new image

@@
 			\centering
-			\includegraphics[height=40mm,width=90mm]{Trilateration_methods.JPG}
+			\includegraphics[height=30mm,width=90mm]{Trilateration_methods.JPG}
 			\caption{The red arrow represents the robot.The 'X' represents the origin of the robot. The blue line shows the traversed path.The star represents the landmark. }
@@
 
-In /cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
+In \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
 It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small.

### 2018-02-16 Paper.tex
Added brief prediction/measurment to EKF
Added a really brief poorly worded description of the update and measurment phase of EKF
Minor Edits
Edits made to paper as per revision R2.

@@
 There are many algorithms used to solve this problem, most using a landmark-based approach.
-The concept of a landmark is identifying a distinguishable feature in the environment through camera or laser rangefinder and estimating the distance and orientation of that landmark relative to the robot.
-Then, as the robot traverses the environment, it can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
-In most SLAM applications, references to the map is synonymous with the locations of the landmarks.
+Landmarks are distinguishable feature in the environment which can be observed through devices such as a camera or a laser rangefinder.
+Said devices are used to estimate the distance and orientation of the landmark relative to the robot.
+As the robot traverses the environment it continues to observe and collect landmarks.
+The sensed distance and angle from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map.
+		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
+		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.
 
@@
 Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively.
-While these beacons provide distance estimations to the robotic vehicle, they do not inherently provide location information as with GPS.
+These beacons provide distance estimations to the robotic vehicle, but do not inherently provide location information as with GPS.
 However, these distances are often still useful as they can be used to compensate for the drift that occurs from measuring a vehicle's displacement through integration of inertial sensor readings.
@@
 
-		This paper surveys the most popular techniques in RO-SLAM applications.
+		This paper surveys state of the art RO-SLAM applications.
 Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of these beacons in Section \ref{beacon initialization}.
@@
 	\label{range only sensors}
-		There are a variety of range sensors which can be utilized as beacons for RO-SLAM.
-Beacons refer to any device which involves a signal transmission that can be used for the range estimation without line of sight.
+		There are a variety of range sensors which can be utilized for RO-SLAM.
+These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight.
 The most popular beacons can largely be broken down into two categories: acoustic based and radio frequency based.
@@
 		\subsection{Radio Frequency}
-			Radio frequency encompass a massive spectrum of devices capable of transmitting or receiving transmission on the radio frequency.
+			Radio frequency encompass a massive spectrum of devices capable of transmitting or receiving transmission on the electromagnetic frequency.
 There are two methods primarily utilized to determine distance from radio frequency.
@@
 
-			Ultra-wideband radios are another popular choice.
-One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms.
-\cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
-
-			Wireless Fidelity (wi-fi)  is another choice being explored by man researchers as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
+			Wireless Fidelity (wi-fi)  is the most popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
 \cite{Youssef2005} presents a Horus system with the aim of high accuracy and low computation cost for wireless local area network location determining.
@@
 \cite{Rea2017} designed a new method for filtering range measurment specifically designed with the large noise found in indoor WiFi radios in mind.
+
+			Ultra-wideband radios are another popular choice.
+One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms.
+\cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
 
@@
 		\label{beacon initialization}
-		The core motivation of SLAM algorithms is no a priori knowledge of the operating environment.
-This includes locations of landmarks, including beacons.
+		The core motivation of SLAM algorithms is the exclusion of a priori knowledge of the operating environment.
+This includes locations of landmarks.
 Because of this, landmarks are appended to the map as they are discovered in traditional SLAM algorithms, using the robot's estimated pose and the sensed distance and orientation to estimate an initial position of the landmark.
@@
 	\subsubsection{Trilateration}
+		Trilateration refers to the process of using the distance to at least three devices at known locations in order to estimate the location of a fourth device.
+Methods generally utilize the geometry of circles and triangles in order to accomplish this.
 \cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection.
@@
 	\subsubsection{Particle filter}
-		This takes a more probabilistic approach to estimating the initial location of the beacons.
-As mentioned in\cite{Thrun2002a} initially the entire space is represented by particles.
+		Particle filters takes a probabilistic approach to estimating the initial location of the beacons.
+As mentioned in \cite{Thrun2002a}, initially the entire space is represented by particles.
+Particles refer to collection of sample states.
 These particles are resampled based on importance weights every iteration.
@@
 Eventually the particle set converges to the accurate location of the beacons.
-Though this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
+Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
 
 	\subsection{Undelayed/Online initializations}
-		In this case the robot simultaneously initializes and localizes itself and the beacons as it moves
-		as mentioned in \cite{Caballero2010}.
+		With undelayed/online initializations simultaneously initializes and localizes itself and the beacons as it moves, as mentioned in \cite{Caballero2010}.
 A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.
 This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden.
-\cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane.
+\cite{Geneve2015} presents a method that models a Gaussian mixtures for beacon initialization in EKF.
+This method only uses two hypotheses and a Cartesian plane.
 \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation.
 The paper proposes that under different circumstances the landmark could be represented using different parameters.
+This representation would lead to reduced computation cost for large scale range only SLAM as opposed to the high computation cost of multiple hypothesis landmark representations.
 Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach.
@@
 The derivation of the EKF is very well documented, as such, detailed explanations can be viewed from a variety of sources such as: \cite{Thrun2002}, \cite{Ribeiro2004}, and \cite{Haykin2001}.
+Generally, EKF can be broken up into two phases, the prediction and the measurement phase.
+The prediction phase updates the state vector based on control inputs and additive Gaussian noise.
+The measurement phase updates the state vector based observed landmarks with additive Gaussian noise.
+	%NOTE THIS PART ABOUT PREDICTION AND MEASURMENT PHASE IS SUPER ROUGH
+
 	 When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation \cite{Thrun2002}.
-This distinction becomes important when examining range only SLAM (RO-SLAM) where only the range to a landmark, or the range between landmarks, is known.
-This restriction means that landmarks often need to be manufactured, such as the beacons discussed in previous sections, and physically placed in an environment.
-However, that does not mean that the exact location of the landmarks, or even there initial existence, is recognized.
+This distinction becomes important when examining range only SLAM where only the range to a landmark, or the range between landmarks, is known.
+	 %This restriction means that landmarks often need to be manufactured 
+	 %add rererence here...
+	 %, such as the beacons discussed in previous sections, and physically placed in an environment. 
+	 In addition, the exact location of the landmarks, or even there initial existence, is not always known at startup.
 Initialization is a critical element in many algorithms that make use of the EKF.
@@
 \cite{Herranz2014} presents a comparison of the ROP-EKF method presented by \cite{Djugash2008}, to a smoothing and mapping method presented by \cite{Dellaert2006}.
-Experimentation conducted by \cite{Herranz2014} on and indoor and outdoor environment show an improvement in the results of the SAM method over ROP EKF.
+Experimentation conducted by \cite{Herranz2014} on and indoor and outdoor environment show an improvement in the results of the smoothing and mapping (SAM) method over ROP EKF.
 
@@
 
-	A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem.
+	A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for unmanned aerial systems dealing with the 3D RO-SLAM problem.
 The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in.
@@
 
-	It is explored by \cite{Kehagias2006} how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at and then applied to solve the RO SLAM problem.
+	\cite{Kehagias2006} explores how interpolation can be used to generate range data that is equally spaced over time as opposed to the irregular time intervals that range data is typically received at and then applied to solve the RO SLAM problem.
 The method is tested on the EKF and an batch optimization algorithm with a simulated and physical robot.
@@
 \subsection{Sparse Extended Information Filters}
-Need to add references
 
 Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
-An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}.
-In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the Gaussians in their conical parameterization which comprises of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa.
-Hence they are dual to each other.
-Sparse Extended information filters is derived from the  information filter but it maintains a sparse representation of the information matrix.
-This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}
+An information filter (IF) algorithm is mentioned in\cite{Torres-Gonzalez2014}.
+In EKF the Gaussians are represented in the form of their moments, mean and variance, whereas in a information filter the Gaussians are in their conical parameterization which comprises of an information matrix and information vector.
+%Hence what is computationally complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
+Sparse Extended information filters are derived from the  information filter but it maintains a sparse representation of the information matrix.
+This makes the SEIF more scalable and efficient as show in \cite{Torres-Gonzalez2014}.
 
-The information filter stores the relation between any 2 state elements in the information matrix also known as links.
-The higher the value of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robots state.
-SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved .
+The information filter stores the relation between any two state elements in the information matrix also known as links.
+The higher the value of the link the stronger is the relationship between the two state variables and the more it is gonna effect the robots state.
+SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved.
 
-In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons.
-Here the robot computes the prediction stage of the iteration, send the information to the beacons where they compute the update of the process.
-Hence the computer burden on the robot is reduced.
-In addition, they factored in inter beacon measurements to reduce uncertainty even further.
-In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.
+In \cite{Torres-Gonzalez2014} the computational complexity is reduced by utilizing the computational capabilities of the nodes or radio  beacons.
+Here the robot computes the prediction stage of the iteration, sends the information to the beacons where the update process is completed.
+Hence the computation burden on the robot is reduced.
+In addition, inter-beacon measurements are factored in to reduce uncertainty even further.
+In \cite{Torres-Gonzalez2017} the SEIF method is evaluated and compared for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.
 
 \subsection{Particle Filters}      %change the references
-Particles filters are made ue up various monte carlo algorithms.
+Particles filters are a category of monte carlo algorithms.
 they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}.
 In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks.
-It has also been at the core higher dimensional computational problems.
+It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization (THIS IS A FIXED CITATION, PUT ACTUAL CITATION HERE)[2] and the kidnapped robot problem \cite{Engelson1992} which EKF ,in comparison, struggles with.
+At is core, EKF also has higher dimensional computation problems.
+% It has also been at the core higher dimensional computational problems.  
 %Description
@@
 	\centering
-	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
+	\includegraphics[height=50mm,width=95mm]{Particle_filter_method.JPG}
 	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter.

### 2018-02-19 Paper.tex
Added Conclusion

@@
 SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information.
-The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is with respect to a global frame, or map, and building a map requires knowledge of the robot's location.
+The SLAM problem is a chicken-and-egg type problem, where the pose of the robot has to be with respect to a global frame, or map, and building a map requires knowledge of the robot's pose.
 There are many algorithms used to solve this problem, most using a landmark-based approach.
@@
 		This paper surveys state of the art RO-SLAM applications.
-Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of these beacons in Section \ref{beacon initialization}.
+Before discussing RO-SLAM techniques, the different types of range sensors are introduced in Section \ref{range only sensors}, followed by initialization of range beacons in Section \ref{beacon initialization}.
 Solutions to the RO-SLAM state estimation problem are covered in Section \ref{methods and their implementations}.
@@
 	\label{range only sensors}
-		There are a variety of range sensors which can be utilized for RO-SLAM.
+		There are a variety of sensors which can be utilized as range beacons for RO-SLAM.
 These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight.
-The most popular beacons can largely be broken down into two categories: acoustic based and radio frequency based.
+The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based.
 These beacons serve as landmarks within larger SLAM algorithms.
@@
 		\subsection{Radio Frequency}
-			Radio frequency encompass a massive spectrum of devices capable of transmitting or receiving transmission on the electromagnetic frequency.
+
+			Radio frequency encompass a extensive spectrum of devices capable of transmitting or receiving using radio frequencies (RF).
 There are two methods primarily utilized to determine distance from radio frequency.
@@
 		\subsection{Delayed/Offline initializations}
-			These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks.
-This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles.
-Localization can be performed only once a accurate estimations of the beacons are made.
-There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman}, a posed based ekf as mentioned in \cite{Webster2012}, a moving horizon estimation as mentioned in \cite{Vallicrosa2014a} etc.
-The most popular ones are mentioned below.
+			Delayed/offline initializations are methods which attempt to localize the beacon prior to incorporating it into the active SLAM algorithm.
+Some SLAM algorithms require an approximate location of each landmark before being incorporated into the algorithm.
+Since beacons only provide range data, the location of the beacon is not known upon first observation, and must be initialized.
+These processes which determine the initial estimated location of the beacon before being added to the SLAM algorithm are known as delayed or offline initializations.
+These initialization methods can be undesirable as they require the SLAM algorithm to run without corrective measurements until the first beacon is initialized.
+Presented in this section are the most prevalent methods for offline beacon initialization.
 
@@
 Particles refer to collection of sample states.
-These particles are resampled based on importance weights every iteration.
-There are several resampling methods mentioned in \cite{Li2015}.
+These particles are re-sampled based on importance weights every iteration.
+There are several re-sampling methods mentioned in \cite{Li2015}.
 Eventually the particle set converges to the accurate location of the beacons.
 Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
+
+			\subsubsection{Other Methods}
+			 	The methods presented above tend to be the more common approaches, however, there are several offline algorithms that perform offline localization.
+A least squares approach is described in \cite{Newman}, a posed-based EKF (Extended Kalman Filter) method is mentioned in \cite{Webster2012}, and a moving horizon estimation is presented in \cite{Vallicrosa2014a}.
+These methods have also proven effective for the beacon types used in their respective applications.
 
@@
 	\label{conclusion}
+	This paper has introduced the motivation and practicality of range-only SLAM approaches.
+The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms.
+The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.
+
+	Given the maturity of SLAM as a research field, the area of RO-SLAM still has lots of area to explore.
+Most of the common methodologies presented here focus on adapting traditional SLAM algorithms to accommodate only range data.
+While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with uniques solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.
 

### 2018-02-25 Paper.tex
Revisions to particle filter

@@
 			\subsubsection{Particle filter}
-				Particle filters takes a probabilistic approach to estimating the initial location of the beacons.
-As mentioned in \cite{Thrun2002a}, initially the entire space is represented by particles.
-Particles refer to collection of sample states.
+				Particle filters takes a probabilistic approach to estimating the initial location of the beacons as mentioned in \cite{Thrun2002a}.
+Here, a particle refers to a  possible hypothesis of position of the landmark.
+
+				Initially the robot assumes global uncertainty through a set of particles that are distributed all over the map as shown in Fig 2.(a).
+Hence the position of the landmarks are uncertain.
+As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one as shown in Fig.2(b).
+There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the initial location of the landmarks as shown in Fig.2(c).
+				\begin{figure}[h!]
+					\centering
+					\includegraphics[height=35mm,width=90mm]{Particle_filter_method.JPG}
+					\caption{The leftmost image describes the state of the robot when it just initializes the particle filter.
+The particles are uniformly distributed.
+The image in the center describes the particle filter after a couple of iterations.
+Only the particles which have a higher probability are re sampled.
+The image on the right shows the particle filter eventually converging to estimate the landmark location.
+}
+
+				\end{figure}
+				Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.
+				Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$.
+It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$.
+Eventually the particle filter converges to give us the true positioning of the landmarks.
 				 These particles are re-sampled based on importance weights every iteration.
@@
 Eventually the particle set converges to the accurate location of the beacons.
-Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
 
@@
 Particles filters are a category of monte carlo algorithms.
-they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}.
+They are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}.
 In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
-It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization (THIS IS A FIXED CITATION, PUT ACTUAL CITATION HERE)[2] and the kidnapped robot problem \cite{Engelson1992} which EKF ,in comparison, struggles with.
+It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization \cite{Borenstein1996} and the kidnapped robot problem \cite{Engelson1992} which EKF, in comparison, struggles with.
 At is core, EKF also has higher dimensional computation problems.
@@
 %Description
-Initially robot assumes global uncertainty through a set of particles that are distributed all over the map.
-Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one.
-There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
-\begin{figure}[h!]
-	\centering
-	\includegraphics[height=50mm,width=95mm]{Particle_filter_method.JPG}
-	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter.
-The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations.
-Only the particles which have a higher probability are re sampled.
-The image on the right shows the particle filter eventually converging to estimate the robot location.
-}
+As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem) where the robot is randomly picked up and placed in a unknown environment.
+EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}.
 
-\end{figure}
-Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.
-re sampling methods depending on computational complexities.
-After some iterations only th   p
-Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$.
-It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$.
-Eventually the particle filter converges to give us the true positioning of the robot.
-
-As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem ) where the robot is randomly picked up and placed in a unknown environment.
-EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}
+It works in a similar way to the particle filter initialization procedure mentioned before, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
 As the number of particles increases the computational complexity of the filter too increases.
@@
 It also solves the data association problem previously unsolved by EKF.
+Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
 
-In \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
+   \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
 It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small.

### 2018-02-27 Paper.tex
Revert "Random Fixes to Body"
This reverts commit bf1d10d3d2648868501859948f351b17aa3b1ecc.

@@
 The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based.
+These two types of sensors both rely on the same principles for measuring distances, which is either by signal time of flight, or signal attenuation through propagation through each respective medium.
 These beacons serve as landmarks within larger SLAM algorithms.
@@
 
-			Ultra-wideband radios are another popular choice.
-One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms.
-\cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
-
-			 \cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to wireless sensor networks.
+			 Another popular wireless standard often used in wireless ranging and localization applications is IEEE 802.15.4, which has been largely popularized by the ZigBee protocol.
+In contrast with IEEE 802.11 WiFi standards, 802.15.4 is focused on shorter-ranged, low power peer-to-peer networks, thus making it a widely used protocol in Wireless Sensor Networks (WSN).
+\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.
 \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more.
-\cite{Baronti2007} specifically focuses on state of the art 802.15.4 and ZigBee standards.
+\cite{Baronti2007} specifically focuses on wireless sensors utilizing ZigBee standards.
 \cite{Xia2011} examines the limitations of original IEEE 802.15.4 MAC and reviews adaptive methods that have been used to overcome these limitations.
 \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.
+
+			 Ultra-wideband (UWB) radios are another popular choice.
+One attractive feature of currently used ultra-wide band transmitters and receivers is the ability resolve multipath error ,which is a common obstacle with indoor environments, without the use of extensive algorithms due to its use of multiple frequencies across a large bandwidth.
+\cite{Gezici2005} presents an analysis of time of arrival based localization estimations with ultra-wide band.
 

### 2018-02-27 Paper.tex
Revert "Revert "Random Fixes to Body""
This reverts commit da946e5fdae3a8ecb4cd4be59d18446e59c383d6.

@@
 			\subsubsection{Particle filter}
-				Particle filters takes a probabilistic approach to estimating the initial location of the beacons as mentioned in \cite{Thrun2002a}.
-Here, a particle refers to a  possible hypothesis of position of the landmark.
+				The particle filter takes a probabilistic approach to estimating the initial location of the beacons as mentioned in \cite{Thrun2002a}.
+Here, a particle refers to a  possible hypothesis of position of the beacon/landmark.
 
-				Initially the robot assumes global uncertainty through a set of particles that are distributed all over the map as shown in Fig 2.(a).
-Hence the position of the landmarks are uncertain.
-As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one as shown in Fig.2(b).
-There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the initial location of the landmarks as shown in Fig.2(c).
+				Initially the robot assumes global uncertainty through a set of particles that are uniformly distributed over the map as shown in Fig 2.(a).
+Hence the position of the beacons are uncertain.
+As the robot moves around and measures sensor data it re-samples the particle set based on computed weights.
+Particles that match sensor data are assigned higher probabilistic weights and are therefore more likely to be re-sampled each iteration.
+Fig.2(b) illustrates this, as particles with hypothesized beacon locations far from the true location do not match the sensed range and over time are eliminated from the set.
+After many iterations only the particles which have a high degree of probability  remain and eventually converge to the true location of the beacons as shown in Fig.2(c).
+There are several re-sampling methods which are discussed in \cite{Li2015}.
 				\begin{figure}[h!]
@@
 Only the particles which have a higher probability are re sampled.
-The image on the right shows the particle filter eventually converging to estimate the landmark location.
+The image on the right shows the particle filter eventually converging to estimate the beacon location.
 }
@@
 It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$.
-Eventually the particle filter converges to give us the true positioning of the landmarks.
+Eventually the particle filter converges to give us the true positioning of the beacons.
 				 These particles are re-sampled based on importance weights every iteration.
@@
 If the initialization is inaccurate then the convergence to a correct estimation becomes much more difficult for the filter.
-The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
+The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008} \cite{Shue2017}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
 This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via methods with EKF mind.
@@
 They are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}.
-In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
+In  early applications, particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data.
 It is considered better and more robust to conventional estimation methods because of its ability to solve the global localization \cite{Borenstein1996} and the kidnapped robot problem \cite{Engelson1992} which EKF, in comparison, struggles with.
@@
 %Description
-As mentioned in \cite{Thrun2002a} particle filters outperform EKF in applications involving global localization (the kidnapped robot problem) where the robot is randomly picked up and placed in a unknown environment.
+As mentioned in \cite{Thrun2002a}, particle filters outperform EKF in applications involving global localization (the kidnapped robot problem) where the robot is randomly picked up and placed in a unknown environment.
 EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}.
 
-It works in a similar way to the particle filter initialization procedure mentioned before, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
+It works in a similar way to the particle filter initialization procedure mentioned in Section \ref{beacon initialization}, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
+
 As the number of particles increases the computational complexity of the filter too increases.

### 2018-02-27 Paper.tex
FINAL SUBMISSION

@@
 In contrast with IEEE 802.11 WiFi standards, 802.15.4 is focused on shorter-ranged, low power peer-to-peer networks, thus making it a widely used protocol in Wireless Sensor Networks (WSN).
-\cite{Baronti2007}, \cite{Khanafer2014}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.
+\cite{Baronti2007}, \cite{Khanafer2014},\cite{Shue2013}, \cite{Akyildiz2002}, and \cite{Xia2011} each present surveys relating to WSNs.
 \cite{Baronti2007} and \cite{Akyildiz2002} both provide very well developed surveys that discuss hardware, protocols, standards, security, energy efficiency and much more.
@@
 \cite{Khanafer2014} specifically survey methods meant to improve the performance of IEEE 802.15.4 MAC protocol.
+\cite{Shue2013} surveys the application of robotics in wireless sensors by examining topics such as data mules, sensor failures, and node localization.
 
@@
 				Trilateration refers to the process of using the distance to at least three devices at known locations in order to estimate the location of a fourth device.
-Methods generally utilize the geometry of circles and triangles in order to accomplish this.
+Methods generally utilize the geometry of circles and triangles in order to accomplish this \cite{Johnson2017}.
 \cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection.

### 2018-08-20 Paper.tex
Added comments for future changes
Added some comments on how to make future changes and revised some grammer/structure

@@
 
+	%The end of the abstract, I think, needs a better explanation of the survey other than stating that RO-SLAM techniques will be explored, ie: a more unifying theme
 	\begin{abstract}		
 		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM).
-In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, within the environment through sensors such as cameras and laser rangefinders.
-Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation proses of the robot's pose and the landmark locations within the map.
-However, some applications use landmarks which are only capable of providing range information, such as wireless and acoutstic beacons.
-In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors (RO-SLAM) is explored.
+In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders.
+Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation processes of the robot's pose and the landmark locations within the map.
+However, some applications use landmarks which are only capable of providing range information, such as wireless and acoustic beacons.
+In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors is explored.
 	\end{abstract}
@@
 	\section{Introduction} 
-		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications.
-SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information.
-The SLAM problem is a chicken-and-egg type problem, where the pose of the robot has to be with respect to a global frame, or map, and building a map requires knowledge of the robot's pose.
-There are many algorithms used to solve this problem, most using a landmark-based approach.
-Landmarks are distinguishable feature in the environment which can be observed through devices such as a camera or a laser rangefinder.
-Said devices are used to estimate the distance and orientation of the landmark relative to the robot.
+		%Possible way to breakup RO-SLAM methods other than by sensor type: indoor and out door
+
+		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many robotics applications.
+SLAM involves estimating the pose of a mobile robot and building a map of its environment with no priori knowledge of said environment.
+The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is ascertained with respect to a global frame, or map, and the building of a map requires knowledge of the robot's pose.
+There are many algorithms used to solve this problem, many use a landmark-based approach.
+Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder.
+Said devices can be used to estimate the distance and orientation of the landmark relative to the robot.
 As the robot traverses the environment it continues to observe and collect landmarks.
-The sensed distance and angle from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map.
+The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map.
 		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
@@
 
-		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry.
+		%A bit of a jarring transition.
+The goal is to introduce RO-SLAM and explain the difference between RO-SLAM and SLAM.
+The paragraph acomplishes that but maybe there is a smoother way to go about it.
+Also might need an explanation of location information and specifically how it differentiates from distance information
+		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry. %ADD A CITATION
 		While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors.
@@
 
-		While the loss of orientation from traditional, vision based landmarks prevents refinement of the robot's orientation, range only beacons solve two major problems encountered in traditional landmark-based approaches: landmark association and landmark scaling.
+		While the loss of orientation from traditional, vision based landmarks  proves to be a detriment, range only beacons solve two major problems encountered in traditional landmark-based approaches: landmark association and landmark scaling.
 The landmark association problem occurs when a detected landmark has similar features to previously recorded landmark and is mistaken for the other, generating huge errors in the estimation of both the robot and the landmark.
@@
 Since the robot can observe the landmarks more often, it doesn't need to add nearly as many to ensure accurate position estimation.
+%Need a citatation to back that claim up
 
+		%Eh... probably some better phrasing for this paragraph
 		This paper surveys state of the art RO-SLAM applications.
@@
 	\label{range only sensors}
-		There are a variety of sensors which can be utilized as range beacons for RO-SLAM.
-These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without line of sight.
+		There are a variety of sensors which can be utilized as range-only beacons for RO-SLAM.
+These range sensors refer to any device which involves a signal transmission that can be used for the range estimation without requiring line of sight.
 The most popular sensors can largely be broken down into two categories: acoustic based and radio frequency based.
-These two types of sensors both rely on the same principles for measuring distances, which is either by signal time of flight, or signal attenuation through propagation through each respective medium.
-These beacons serve as landmarks within larger SLAM algorithms.
-The following section surveys the different types of sensors which can be utilized as range beacons.
+These two types of sensors both largely rely on the same principles for measuring distances, which are either signal time of flight, or signal attenuation through propagation through each respective medium.
+These beacons serve as the landmarks within the RO-SLAM algorithms and impact how the algorithms are implemented.
 
+		%I think this section could use some more details.
 		\subsection{Acoustic}
 
-			Acoustic ranging systems are primarily used with autonomous underwater vehicles (AUV) and sonar beacons that operate in underwater locations.
-The reason for this that radio waves experience strong attenuations, especially in salt water environments.
-As \cite{Partan2007} states, the issue of attenuations makes radio waves extremely impractical, thus making acoustics the logical alternative.
-Acoustic still suffer from a range of problems such as multipathing and propagation delays, but are one of the only meaningful alternatives.
-Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a 2D environment versus a 3D environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.
+			Acoustic ranging systems are largely used with autonomous underwater vehicles (AUV) that operate in underwater locations.
+The reason for this is that radio waves experience strong attenuations in salt water environments.
+As Partan states, the issue of attenuation makes radio waves extremely impractical, thus making acoustics the logical alternative \cite{Partan2007}.
+Acoustics still suffer from a range of problems such as multipathing and propagation delays, but compared to the alternatives they perform adequately in underwater environments.
+Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a two dimensional versus a three dimensional environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.
 
+		  	%Ehhhhh.. This section... I dunno if this section is necissary
 			A unique implementation of an underwater acoustic beacon is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}.
 These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates.
-The distance to an agent and the transmitting beacon can be determined via time of flight from the transmissions.
+The distance between an agent and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon.
 A localization implementation using these beacons was accomplished by \cite{Erol2008}.
-
-	%		  	\begin{figure}[h!]
-	%				\centering
-				%	\includegraphics[width=90mm]{DNR.png}
-	%				\includegraphics[width=90mm]{DNR.png}	
-	%				\caption{DNR being used to implement Dive and Rise Localization  \cite{Erol-Kantarci2011}}
-	%				\label{DNR}
-	%			\end{figure}
 
@@
 
-			Radio frequency encompass a extensive spectrum of devices capable of transmitting or receiving using radio frequencies (RF).
-There are two methods primarily utilized to determine distance from radio frequency.
-One is by examining the received signal strength indicator (RSSI) and the other is the by measuring the time of flight of the signal.
+			Radio frequency encompasses an extensive spectrum of devices capable of transmitting or receiving signals using radio frequencies (RF).
+There are two methods commonly utilized to determine distance from radio frequency.
+One is by examining the received signal strength indicator (RSSI) and the other is by measuring the time of flight of the signal.
 A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.
 \cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.
-As a mobile robot moves throughout an environment it emits a query to which any RF tags that are within the transmission range respond.
+As a mobile robot moves throughout the environment it emits a query to which any RF tags that are within the transmission range respond.
 The robot then estimates the distance to the tag based on the delay.

### 2018-11-05 Paper.tex
Minor fixes
Mostly changing the wording of the abstract and introduction paragraph to be more cohesive

@@
 In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders.
-Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation processes of the robot's pose and the landmark locations within the map.
-However, some applications use landmarks which are only capable of providing range information, such as wireless and acoustic beacons.
-In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors is explored.
+Sensing these landmarks provide the robot with information such as range and bearing to the landmark, which are used in various algorithms responsible for determining the robot's pose and the landmark locations within the map.
+However, some applications have the restriction of using landmarks which are only capable of providing range information, such as wireless and acoustic beacons.
+Attempting to simultaneously localize and map with this restriction is termed Range-Only Simultaneous Localization and Mapping (RO-SLAM).
+This paper examines recent advances in the algorithms and technologies utilized to accomplish RO-SLAM.
+
+		% In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors is explored.
 	\end{abstract}
@@
 
-		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many robotics applications.
-SLAM involves estimating the pose of a mobile robot and building a map of its environment with no priori knowledge of said environment.
-The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is ascertained with respect to a global frame, or map, and the building of a map requires knowledge of the robot's pose.
-There are many algorithms used to solve this problem, many use a landmark-based approach.
+		The task of Simultaneous Localization and Mapping (SLAM) is a common aspect in many robotics applications.
+SLAM involves estimating the pose of a robot while simultaneously building a map of its environment with no priori knowledge of said environment.
+This task can be represented as a causality dilemma, where the pose of the robot is ascertained with respect to a global frame, or map, and the creation of a map requires knowledge of the robot's pose.
+There are a variety algorithms used to solve this problem, many of which use a landmark-based approach.
 Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder.
-Said devices can be used to estimate the distance and orientation of the landmark relative to the robot.
-As the robot traverses the environment it continues to observe and collect landmarks.
+Said devices can be used to measure propeties such as the distance or orientation of the landmark relative to the robot.
+As the robot traverses the environment it continues to observe and collect landmarks while simultaneously building a map and localizing itself within the map.
 The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map.

### 2018-11-07 Paper.tex
Very very minor edits
Just some very slight grammer edits on the introduction

@@
 Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder.
-Said devices can be used to measure propeties such as the distance or orientation of the landmark relative to the robot.
+Said devices can be used to measure propeties such as the distance or bearing of the landmark relative to the robot.
 As the robot traverses the environment it continues to observe and collect landmarks while simultaneously building a map and localizing itself within the map.
-The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map.
+The sensed distance and bearing to each landmark can be combined with other factors like odometry readings to get an refined estimation of the robot pose and map.
 		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map.
-		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.
+	%	In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.
 
-		%A bit of a jarring transition.
-The goal is to introduce RO-SLAM and explain the difference between RO-SLAM and SLAM.
-The paragraph acomplishes that but maybe there is a smoother way to go about it.
-Also might need an explanation of location information and specifically how it differentiates from distance information
-		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry. %ADD A CITATION
+		%Ohhhh my good  this feels so jaring to read. I don't think odometry was ever properly introduced either
+		In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) measurements are used to help localize a vehicle. %ADD A CITATION
 		While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors.
 However, GPS isn't available in all environments, such as indoors and underwater.
-Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively.
-These beacons provide distance estimations to the robotic vehicle, but do not inherently provide location information as with GPS.
+Instead, wireless signals and sonar beacons are often are utilized.
+These beacons provide range data, but do not inherently provide location information as with GPS.
 However, these distances are often still useful as they can be used to compensate for the drift that occurs from measuring a vehicle's displacement through integration of inertial sensor readings.

### 2018-11-07 Paper.tex
Added to EKF section
Short summary added to Implementation section and EKF section. Short conlcusion written for EKF section

@@
 	\label{methods and their implementations}
-
+	The following implementations are broken down into categories based on the general algorithm that is used by the implementation to do RO-SLAM.
+The concept behind the algorithm is summarized in each category followed by a discussion of implementations that incorporates said algorithm.
+Each category concludes by examining the problems that current implementations are focusing on and theorizing about possible future directions for research.
 	\subsection{EKF}
@@
 The measurement phase updates the state vector based observed landmarks with additive Gaussian noise.
-	%NOTE THIS PART ABOUT PREDICTION AND MEASURMENT PHASE IS SUPER ROUGH
 
 	 When used to solve SLAM the map applied to the EKF is a feature based map, meaning it is composed of observable features (landmarks) which can be distinguished between during re-observation \cite{Thrun2002}.
-This distinction becomes important when examining range only SLAM where only the range to a landmark, or the range between landmarks, is known.
+This distinction becomes important when examining RO-SLAM where only the range to a landmark, or the range between landmarks, is known.
 	 %This restriction means that landmarks often need to be manufactured 
@@
 	 %, such as the beacons discussed in previous sections, and physically placed in an environment. 
-	 In addition, the exact location of the landmarks, or even there initial existence, is not always known at startup.
+	 In addition, the exact location of the landmarks, or even there initial existence, is not always known at the beginning of runtime.
 Initialization is a critical element in many algorithms that make use of the EKF.
-If the initialization is inaccurate then the convergence to a correct estimation becomes much more difficult for the filter.
+If the initialization is inaccurate then the convergence to a correct estimation can become much more difficult.
 The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008} \cite{Shue2017}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
-This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO SLAM, as well as examine improvements to the general RO SLAM problem that are applied via methods with EKF mind.
+This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO-SLAM.
 
+	%Underwater implementations
 	A system for robust range only localization was prosed by \cite{Olson2006}.
@@
 
+	%AUV implementations
 	\cite{Kurth2003} presents a comparison of how three methods process a collected data set.
@@
 
-	It is explained by \cite{Torres-Gonzalez2015} that methods utilizing inter beacon measurment should incorporate measurements with a configurable number of hops between beacons.
+	It is explained by \cite{Torres-Gonzalez2015} that methods utilizing inter beacon measurements should incorporate measurements with a configurable number of hops between beacons.
 This allows for the robot to gather range data from beyond the extent of the robots sensors.
@@
 
-	\cite{Djugash2006} presents a comparison of multiple RO SLAM methods utilized in two scenarios.
+	\cite{Djugash2006} presents a comparison of multiple RO-SLAM methods utilized in two scenarios.
 One scenario involves the case where the robot only has access to range information between itself and beacons at unknown locations.
@@
 Several separate methods were compared in the given scenarios utilizing a data set and experimentation.
-The first method utilizes the Kalman filter in the case where only measurment between moving and stationary beacons are considered.
+The first method utilizes the Kalman filter in the case where only measurement between moving and stationary beacons are considered.
 Another method specifically uses the beacon to beacon measurements with an online Kalman filter.
@@
 In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+
+	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements.
+Many implementations now seek to measure the distance between beacons and incorporate those measurements into existing EKF algorithms.
 

### 2018-11-07 Paper.tex
Slight rewording

@@
 	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements.
-Many implementations now seek to measure the distance between beacons and incorporate those measurements into existing EKF algorithms.
+Many implementations now have beacons measure ranges to other beacons in addition to the robot.
+These beacon to beacon range measurements are then incorporated into existing EKF algorithms.
 

### 2018-11-07 Paper.tex
Started editing sensor section
Up to the beginning of Wi-Fi

@@
 These two types of sensors both largely rely on the same principles for measuring distances, which are either signal time of flight, or signal attenuation through propagation through each respective medium.
-These beacons serve as the landmarks within the RO-SLAM algorithms and impact how the algorithms are implemented.
+These beacons serve as the landmarks within the RO-SLAM algorithms map and can have a significant impact how the algorithms are implemented.
 
 		%I think this section could use some more details.
+
+		%HOLY moly does acostic sensors need mor details
 		\subsection{Acoustic}
@@
 Acoustics still suffer from a range of problems such as multipathing and propagation delays, but compared to the alternatives they perform adequately in underwater environments.
-Papers such as those by \cite{Erol-Kantarci2011} and \cite{Akyildiz2005} explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a two dimensional versus a three dimensional environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.
+For those seeking additional information about the constraints imposed by underwater environments on acoustic sensors see \cite{Erol-Kantarci2011} and \cite{Akyildiz2005}.
+These papers explore a wide variety of issues and possible solutions that relate to acoustic sensors, such as the added complexity of assuming a two dimensional versus a three dimensional environment, or the design challenges that accompany underwater deployment with regards to spatial correlation and power consumption.
 
 		  	%Ehhhhh.. This section... I dunno if this section is necissary
-			A unique implementation of an underwater acoustic beacon is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}.
+			A unique implementation of an underwater acoustic beacons is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}.
 These DNR beacons rise to the surface, receive their location through GPS, then sink into the water and transmit their coordinates.
-The distance between an agent and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon.
+The distance between an robot and the transmitting beacon can be determined via time of flight from the transmissions and used in conjunction with the GPS location to determine a refined location for the beacon.
 A localization implementation using these beacons was accomplished by \cite{Erol2008}.
@@
 
-			Radio frequency encompasses an extensive spectrum of devices capable of transmitting or receiving signals using radio frequencies (RF).
+			This subsection encompasses an extensive spectrum of devices capable of transmitting or receiving signals using radio frequencies (RF).
 There are two methods commonly utilized to determine distance from radio frequency.
@@
 A system presented by \cite{Padmanabhan2000} processes RF signal strength and utilizes nearest neighbors heuristics to achieve localization based on said signal strength.
-\cite{Kurth2003a} describes a method for using very small RF tags as beacons throughout the environment.
+\cite{Kurth2003a} describes a method for using very small RF tags as beacons in an environment.
 As a mobile robot moves throughout the environment it emits a query to which any RF tags that are within the transmission range respond.
@@
 
-			Wireless Fidelity (wi-fi)  is the most popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
-\cite{Youssef2005} presents a Horus system with the aim of high accuracy and low computation cost for wireless local area network location determining.
+			Wireless Fidelity (wi-fi)  is the a popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
+\cite{Youssef2005} presents a system known as Horus with the aim of high accuracy and low computation cost for wireless local area network location determination.
 \cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing.
@@
 	A common focus of many recent papers has been the utilization of beacons for more than just robot to beacon range measurements.
-Many implementations now have beacons measure ranges to other beacons in addition to the robot.
+Such implementations now use beacons to perform tasks such as measuring ranges to other beacons in addition to the robot.
 These beacon to beacon range measurements are then incorporated into existing EKF algorithms.
+Beacons are also utilized to off-load certain processing.
 
@@
 	\label{conclusion}
-	This paper has introduced the motivation and practicality of range-only SLAM approaches.
+	This paper has introduced the motivation and practicality of RO-SLAM approaches.
 The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms.

### 2018-11-09 Paper.tex
Added reference to SEIF section
Added paper Robot-Beacon Distributed Range-Only SLAM for Resource-Constrained Operation to the SEIF section and .bib

@@
 
-Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented.
+Information filters work on the same underlying Gaussian belief principle as that of EKF but vary in the way that Gaussian beliefs are represented.
 An information filter (IF) algorithm is mentioned in\cite{Torres-Gonzalez2014}.
@@
 
+%Jeez, this explains the information filter in suuuuch abstract terms
 The information filter stores the relation between any two state elements in the information matrix also known as links.
-The higher the value of the link the stronger is the relationship between the two state variables and the more it is gonna effect the robots state.
-SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved.
+The higher the value of a link, the stronger the relationship between two state variables which in turn affects the robots state.
+SEIF maintains a sparse information matrix by eliminating weak links that are below a certain threshold thus reducing the computational complexity involved.
 
@@
 In \cite{Torres-Gonzalez2017} the SEIF method is evaluated and compared for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.
+\cite{Torres-Gonzalez2017a} extends this method by integrating a distributed information-driven measurement allocation tool with the SEIF to allow for dynamic selection of measurements.
+The end goal being to create a scheme that utilizes robot-beacon and inter-beacon measurements to increase accuracy while maintaining resource-consumption efficiency and scalability.
+Thus, creating a scalable distributed RO-SLAM scheme with a focus towards resource limited operations.
 

### 2018-11-12 Paper.tex
Added more recent references
Added more references to the paper from 2016+.

Citation abrv can be seen on the google doc.

Made minor grammer and spelling edits all over the paper. Some sections still seem to need significant rewording/organization.... but will probably be acceptable even without that.

@@
 		While the loss of orientation from traditional, vision based landmarks  proves to be a detriment, range only beacons solve two major problems encountered in traditional landmark-based approaches: landmark association and landmark scaling.
-The landmark association problem occurs when a detected landmark has similar features to previously recorded landmark and is mistaken for the other, generating huge errors in the estimation of both the robot and the landmark.
-This problem is avoided using beacons, as they have some kind of network address which is broadcast during transmissions, so there is no way to confuse which range is associated with which landmark.
+The landmark association problem occurs when a detected landmark has similar features to previously recorded landmark and is mistakenly identified as the incorrect landmark, generating huge errors in the estimation of both the robot and the landmark.
+This problem can be avoided by many beacons, as often incorporate features such as an constant network address which is broadcast during transmissions, ensuring no way to misidentify which range measurment is associated with which landmark.
+There are some works that examine scenarios where the range only beacons are indistinguishable, such as in \cite{Jaulin2016} , however the majority of works presented in this paper will consider the beacons to be distinguishable.
 The scaling problem occurs when a SLAM algorithm runs for a long time and more and more landmarks are appended to the map.
@@
 
-			Wireless Fidelity (wi-fi)  is the a popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
-\cite{Youssef2005} presents a system known as Horus with the aim of high accuracy and low computation cost for wireless local area network location determination.
-\cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer to process information allowing it to avoid the impact of multipathing.
+			Wireless Fidelity (WiFi)  is the a popular beacon choice as existing networks are already prevalent in many indoor locations and they are generally low cost \cite{Youssef2005} \cite{Sen2013} \cite{Kotaru2015} \cite{Rea2017}.
+\cite{Youssef2005} presents a system ,known as Horus, with the aim of high accuracy and low computation cost for wireless local area network location determination.
+\cite{Sen2013} proposes a method named CUPID which extracts information from the physical layer which is used during processing to alleviate the impact of multipath interference.
 \cite{Kotaru2015} presents a design and implementation for its SpotFi system which can be deployed on top of existing wi-fi infrastructure.
@@
 	\label{methods and their implementations}
-	The following implementations are broken down into categories based on the general algorithm that is used by the implementation to do RO-SLAM.
+	The following methods implementations are broken down into categories based on the general algorithm that was used to accomplish RO-SLAM.
 The concept behind the algorithm is summarized in each category followed by a discussion of implementations that incorporates said algorithm.
-Each category concludes by examining the problems that current implementations are focusing on and theorizing about possible future directions for research.
 	\subsection{EKF}
@@
 If the initialization is inaccurate then the convergence to a correct estimation can become much more difficult.
-The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008} \cite{Shue2017}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
+The EKF has seen a wide variety of implementation ranging from ground based robotics\cite{Djugash2008, Shue2017}, to unmanned air vehicles \cite{Fabresse2016}, and to autonomous underwater vehicles \cite{Olson2006}.
 This section will proceed to give a summary of the various ways EKF has been implemented in regards to RO-SLAM.
@@
 	%Underwater implementations
-	A system for robust range only localization was prosed by \cite{Olson2006}.
+	A system for robust range only localization was proposed by \cite{Olson2006}.
 The system utilized an Autonomous Underwater Vehicle (AUV) and beacons without carefully surveyed locations.
@@
 	%AUV implementations
-	\cite{Kurth2003} presents a comparison of how three methods process a collected data set.
-The methods are a EKF, a sliding batch, and a particle filter.
-The comparison considers the cross-track error, and along track error.
+	A comparison of how an EKF, sliding batch, and particle filter evaluate a dataset based on cross and along track error is presented by \cite{Kurth2003}.
 The results state that the particle filter works well when used to acquire an initial pose estimate, and EKF works well with real-time localization.
-It is suggested that in the future that the two could be switched between when appropriate to improve the overall system.
+It is suggested that in the future that the two could be switched between when appropriate to improve the overall system performance.
 
@@
 
-	\cite{Vallicrosa2015} presents a solution utilizing a Sum of Gaussian (SOG) filter for a single range only beacon.
-It uses multivariate Gaussian mixtures to represent the probability distribution functions of the robot and beacon positions as Gaussian particles which each contain an EKF for vehicle position, velocity, and estimated beacon position.
+	An Sum of Gaussian (SOG) filter, which incorporates EKFs, was presented by \cite{Vallicrosa2015} for solving RO-SLAM using range measurements towards only a single beacon.
+The proposed filter used multivariate Gaussian mixtures to represent the probability distribution functions of the robot and beacon positions as Gaussian particles which each contain an full EKF for vehicle position, velocity, and estimated beacon position.
 The paper presented experimentation where the method was used to map a beacon while correcting the navigation of the vehicle.
@@
 Experimentation conducted by \cite{Herranz2014} on and indoor and outdoor environment show an improvement in the results of the smoothing and mapping (SAM) method over ROP EKF.
+The author of \cite{Herranz2014} continues by conducting a comparison of RO-SLAM filtering algorithms utilized indoors via WiFi based sensors.
+Specifically, EKF, FastSLAM, and SAM are compared in this work \cite{Herranz2016}.
 
@@
 
+	The joint issue of RO-SLAM and navigation is examined by \cite{Miah2018}.
+The author explains that they seek to solve the robot localization, motion control, and mapping problem simultaneously in their work.
+Range measurements are obtained via RSSI from an Xbee radio network and used along with bearing approximations for the measurement model of the EKF.
+Trajectory information gathered from the mobile robot is used for the prediction phase of the EKF.
+The map generated by the EKF is then used to plan the navigation of the robot, which influences the control value used to move mobile robot, which is in turn applied to the prediction step of the EKF.
+Thus, creating a loop which incorporates navigation into the RO-SLAM process.
+
 	\cite{Fabresse2013} presents a solution for the 3D RO-SLAM problem.
@@
 In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}.
-In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurement before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipath.
+In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurement before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipath noise propagation.
 It is then proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors.
-This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation.
+This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving the localization estimation.
 Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot.
 In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).
+The author continues in \cite{R.Fabresse2018} by utilizing an undelayed multi-hypothesis EKF approach based on Gaussian Mixture models and a reduced parametrization of the state vector to improve efficiency for 3D spherical based RO-SLAM.
+The work also incorporates an robot-to-landmark and landmark-to-landmark range only observation model.
 
@@
 Thus, creating a scalable distributed RO-SLAM scheme with a focus towards resource limited operations.
+Further details on and evaluations of the work produced by the author of \cite{Torres-Gonzalez2017,Torres-Gonzalez2017a} can be seen in \cite{Gonzalez2017}.
 
@@
 	% It has also been at the core higher dimensional computational problems.  
-%Description
+	% Description
 	As mentioned in \cite{Thrun2002a}, particle filters outperform EKF in applications involving global localization (the kidnapped robot problem) where the robot is randomly picked up and placed in a unknown environment.
 EKF cannot process negative information, but since particle filters use raw sensor data without any processing they can process negative information\cite{Thrun2002a}.
+It works in a similar way to the particle filter initialization procedure mentioned in Section \ref{beacon initialization}, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
+	%What in the world is negative information??? ^^^ I don't even k
 
-It works in a similar way to the particle filter initialization procedure mentioned in Section \ref{beacon initialization}, but it uses a weighted average of both the possible landmark and robot positions to converge to the actual robot and landmark locations.
-
-As the number of particles increases the computational complexity of the filter too increases.
+	As the number of particles increases the computational complexity of the filter increases.
 In order to address this there were several new methods introduced that  exploit the independence among state variables.
@@
 Although this method of localization can be computationally expensive it is preferred whenever the noise involved is non Gaussian.
+The work presented by \cite{Samyak2018} utilizes particle filters in an attempt to reduce the impact of indoor multipath propagation error.
+A series of beacons operating in the ultrawide band frequency are utilized as landmarks with each represented as a full particle filter in the authors implementation.
+The simulation results provided in \cite{Samyak2018} show an increase in performance of the particle filter method in comparison to several other methods under conditions where multipath propagation is high.
 
-   \cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM.
+  	\cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward in RO-SLAM.
 It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small.

### 2018-11-16 Paper.tex
Cleaning up .bib (slight issue)
Fixing issue with the reference section by making changes to the .bib
However... there is a strange issue where if authors have similar names and appear close in the reference section their name gets replaced with a ------. Not sure if this is intended by IEEEtrans style or not.

Link to someone that wanted to change this: https://tex.stackexchange.com/questions/29381/is-it-normal-for-bibtex-to-replace-similar-author-names-with
Cleaned up Abstract

@@
 Sensing these landmarks provide the robot with information such as range and bearing to the landmark, which are used in various algorithms responsible for determining the robot's pose and the landmark locations within the map.
-However, some applications have the restriction of using landmarks which are only capable of providing range information, such as wireless and acoustic beacons.
+However, some applications have the restriction of using sensors which are only capable of providing range information, such as wireless and acoustic beacons.
+While these sensors solve the issues associated with distinguishing individual landmarks, they are incapable of providing the robot's relative orientation.
 Attempting to simultaneously localize and map with this restriction is termed Range-Only Simultaneous Localization and Mapping (RO-SLAM).
-This paper examines recent advances in the algorithms and technologies utilized to accomplish RO-SLAM.
+This paper exams the common range only sensor types, the challenges associated with initializing range only sensors as landmarks, and the filtering techniques used to create the map and localize the robot and beacons.
 
@@
 
-		  	%Ehhhhh.. This section... I dunno if this section is necissary
+		  	%Ehhhhh.. This section... I dunno if this section is necessary
 			A unique implementation of an underwater acoustic beacons is the Dive'N'Rise (DNR) beacon presented by \cite{Erol2007}.
@@
 The variety of sensors used as range only beacons has been surveyed, along with initialization methods for their incorporation into the common SLAM algorithms.
-The variety of SLAM algorithms as they apply to range-only sensor data are surveyed here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.
+The variety of SLAM algorithms as they apply to range-only sensor data are examined here as well with a focus on the techniques that differentiate them and highlighting their strengths and weaknesses.
 
@@
 Most of the common methodologies presented here focus on adapting traditional SLAM algorithms to accommodate only range data.
-While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with uniques solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.
+While these adapted methods have been proven successful, there is still more research that can be conducted towards solving the RO-SLAM problem with unique solutions which can subvert the need for offline beacon initialization and models designed to handle the multipath errors which plague range sensors.
 
